---
title: "<span style='font-size: 18px'> <span style='text-align: center'> PRISMA-Infant-Outcomes (Issued: 2023-09-25)"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
    df_print: kable
always_allow_html: true

knit: (function(inputFile, encoding) { 
      out_dir <- 'output';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'PRISMA-Infant-Outcomes-Report')) })
---

&nbsp;
&nbsp;
&nbsp;
&nbsp;


##### **Includes data from synapse last updated:** {.unlisted .unnumbered}
##### Kenya : 2023-09-01 {.unlisted .unnumbered}
##### Pakistan : 2023-09-01 {.unlisted .unnumbered}
##### Ghana : 2023-09-01 {.unlisted .unnumbered}
##### Zambia : 2023-09-01 {.unlisted .unnumbered}

```{css, echo=FALSE}
.table caption {
  color: black;
  font-weight: bold;
}
```


```{r, data setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

#*****************************************************************************
#* PRISMA Infant Outcomes -- TABLES 
#* Drafted: 21 September 2023, Stacie Loisate
#* Last updated: 17 April 2023
#*****************************************************************************
library(knitr)
library(tidyverse)
library(reshape2)
library(lubridate)
library(kableExtra)
library(emo)
library(naniar)
#library(dplyr)
library(RColorBrewer)

UploadDate <- "2023-09-01"

path_to_data <- "D:/Users/stacie.loisate/Box/PRISMA-Analysis/Infant-Constructed-Variables/"
path_to_save <- "D:/Users/stacie.loisate/Box/PRISMA-Analysis/Infant-Constructed-Variables/output"

lowbirthweight <- read.csv(paste0(path_to_data, "lowbirthweight.csv"))
preterm_birth <- read.csv(paste0(path_to_data, "preterm_birth.csv"))
sga <- read.csv(paste0(path_to_data, "sga.csv"))

mnh01_constructed <- read.csv(paste0(path_to_data, "mnh01_constructed.csv"))

```

\newpage

### Low birth weight 
**Definition:** Defined as liveborn infant weighing less than 2500g at birth (or within 72 hours of birth). 
<br>
<br>

**To be included in the numerator for this outcome, a participant must have:**
<br>
**1.** Live birth (varname [form]: `INF_DSTERM [MNH11]`).
<br>
**2.** Birthweight measured by PRISMA staff <72 hours following birth OR facility reported birthweight where PRISMA not available (varnames [form]: `BW_EST_FAORRES [MNH11]`, `BW_FAORRES [MNH11]`, `BW_FAORRES_REPORT [MNH11]`).
<br>
**3.** Birthweight measured by PRISMA staff <72 hours following birth OR facility reported birthweight where PRISMA not available (varnames [form]: `BW_EST_FAORRES [MNH11]`, `BW_FAORRES [MNH11]`, `BW_FAORRES_REPORT [MNH11]`).
<br>
<br>

**Common causes for a participant to be marked as "Missing":**
<br>
**-** PRISMA-measured birthweight is missing.
<br>
**-** PRISMA-measured birthweight was taken >= 72 hours following birth.
<br>
**-** Both Facility and PRISMA-measured birthweights are missing.
<br>
<br>

#### Table 1. Low birth weight 
*Values for missing birthweights are also reported in this table. For all variables, 1 indicates "Yes" and 0 indicates "No".*
```{r lbw}

lowbirthweight_tab <- lowbirthweight %>% 
  rowwise() %>% 
  group_by(SITE) %>% 
  summarise(
    "Missing PRISMA, n (%)" = paste0(
      format(sum(MISSING_PRISMA == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(MISSING_PRISMA == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    "Missing Facility, n (%)" = paste0(
      format(sum(MISSING_FACILITY == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(MISSING_FACILITY == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    "Missing PRISMA & Facility, n (%)" = paste0(
      format(sum(MISSING_BOTH == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(MISSING_BOTH == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    
    "LBW < 2500 PRISMA, n (%)" = paste0(
      format(sum(LBW2500_PRISMA == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(LBW2500_PRISMA == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
        "LBW >= 2500 PRISMA, n (%)" = paste0(
          format(sum(LBW2500_PRISMA == 0, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW2500_PRISMA == 0, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
        
        "LBW < 2500 PRISMA - Missing, n (%)" = paste0(
          format(sum(LBW2500_PRISMA == 55, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW2500_PRISMA == 55, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
      
    "LBW < 1500 PRISMA, n (%)" = paste0(
      format(sum(LBW1500_PRISMA == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(LBW1500_PRISMA == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
        "LBW >= 1500 PRISMA, n (%)" = paste0(
          format(sum(LBW1500_PRISMA == 0, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW1500_PRISMA == 0, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
        
        "LBW < 1500 PRISMA - Missing, n (%)" = paste0(
          format(sum(LBW1500_PRISMA == 55, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW1500_PRISMA == 55, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
    
    "LBW < 2500 ANY, n (%)" = paste0(
      format(sum(LBW2500_ANY == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(LBW2500_ANY == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
        "LBW >=2500 2500 ANY, n (%)" = paste0(
          format(sum(LBW2500_ANY == 0, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW2500_ANY == 0, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
        
        "LBW < 2500 ANY - Missing, n (%)" = paste0(
          format(sum(LBW2500_ANY == 55, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW2500_ANY == 55, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
    
    "LBW < 1500 ANY, n (%)" = paste0(
      format(sum(LBW1500_ANY == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(LBW1500_ANY == 1, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
      ")"),
    
        "LBW >= 1500 ANY, n (%)" = paste0(
          format(sum(LBW1500_ANY == 0, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW1500_ANY == 0, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
        
        "LBW < 1500 ANY - Missing, n (%)" = paste0(
          format(sum(LBW1500_ANY == 55, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(LBW1500_ANY == 55, na.rm = TRUE)/sum(M11_INF_DSTERM==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")")
    
    
  )  %>%
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1) 
  
lowbirthweight_tab  %>% 
  `rownames<-` (c(
    "Missing PRISMA Birthweight, n (%)",
    "Missing Facility Birthweight, n (%)",
    "Missing PRISMA & Facility Birthweight, n (%)",
    "1, Yes",
    "0, No",
    "55, Missing",
    "1, Yes ",
    "0, No ",
    "55, Missing ",    
    "1, Yes  ",
    "0, No  ",
    "55, Missing  ",   
    "1, Yes   ",
    "0, No   ",
    "55, Missing   "
  )
  ) %>% 
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 16) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") %>% 
  #pack_rows("Missing Birthweights, n (%)", 1, 3, label_row_css = "color: steelblue;") %>% 
  pack_rows("LBW < 2500 PRISMA, n (%)", 4, 6, label_row_css = "color: steelblue;") %>% 
  pack_rows("LBW < 1500 PRISMA, n (%)", 7, 9, label_row_css = "color: steelblue;") %>% 
  pack_rows("LBW < 2500 Any, n (%)", 10, 12, label_row_css = "color: steelblue;")  %>% 
  pack_rows("LBW < 1500 Any, n (%)", 13, 15, label_row_css = "color: steelblue;") 


```
\newpage

#### Figure 1a. Low birth weight: Histogram of birthweights across sites. 
```{r lbw fig1a}

lowbirthweight_nomissing <- lowbirthweight %>% filter(BWEIGHT_ANY > 0)

ggplot(data=lowbirthweight_nomissing,
       aes(x=BWEIGHT_ANY)) + 
  geom_histogram() + #binwidth = 100
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,5000,500)) + 
  ggtitle("Birthweight by any reporting method, by Site") + 
  ylab("Count") + 
  xlab("Birthweight, g") + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60, 
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank())
  
```
*Figure 1a. Distribution of birthweights across sites. Where PRISMA measurement was not available or if the PRISMA measurement was taken >72 hours following birth, the Facility reported birthweight was used.

\newpage

#### Figure 1b. Low birth weight: Histogram of hours following birth weight was assessed across sites. 
```{r lbw fig1b}

ggplot(data=lowbirthweight,
       aes(x=BW_TIME)) + 
  geom_histogram(binwidth = 1) + 
  #geom_bar(aes(y = after_stat(count/tapply(count, x, sum)[x])),position="stack") +
  #scale_y_continuous(labels = scales::percent) + 
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,72,8)) + 
  ggtitle("Hours from birth infant was weighed, all births, by Site") + 
  ylab("Count") + 
  xlab("Hours") + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60, 
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
  geom_vline(mapping=aes(xintercept=24), linetype ="dashed", color = "red") +
  geom_vline(mapping=aes(xintercept=48), linetype ="dashed", color = "red") + 
  geom_vline(mapping=aes(xintercept=72), linetype ="dashed", color = "red")
  
```
*Figure 1b. Hours following birth weight measurement recorded by PRISMA-trained staff (or Facility reported where PRISMA measurement not available). Report of "0" indicates the measurement was taken <1hr following birth. Dashed lines represent 24, 48, and 72 hour time points. 

\newpage

### Preterm Birth
**Definition:** Preterm Birth prior to 37 completed weeks of gestation* of a birth (live birth or stillbirth). Further classified as: Extremely preterm (<28 weeks), Very preterm (28-32 weeks), Moderate to late preterm (32-37 weeks), and Term (>=37 wks).
<br>
<br>

**To be included in the numerator for this outcome, a participant must have:**
<br>
**1.** Reported gestational age by either LMP or Ultrasound (varnames [form]: `US_GA_WKS_AGE_FTS1-4 [MNH01]`, `US_GA_DAYS_AGE_FTS1-4 [MNH01]`, `GA_LMP_WEEKS_SCORRES [MNH01]`).
<br>
**2.** Valid enrollment ultrasound visit date (varname [form]: `US_OHOSTDAT [MNH01]`)
<br>
**3.** Valid date of birth (varname [form]: `DELIV_DSSTDAT_INF1-4 [MNH09]`).
<br>
**4.** Birth outcome reported as a "Live birth" or "Fetal death" (varname [form]: `BIRTH_DSTERM_INF1-4 [MNH09]`).
<br>
<br>

**Common causes for a participant to be marked as "Missing":**
<br>
**-** Participant is missing a reported GA by Ultrasound AND GA by LMP in MNH01.
<br>
**-** Participant is missing an enrollment ultrasound visit (`TYPE_VISIT=1`).
<br>
**-** Participant has multiple enrollment ultrasound visits (`TYPE_VISIT=1`).
<br>
**-** Default value is used for enrollment ultrasound visit date (`US_OHOSTDAT=07-07-1907`). 
<br>
**-** Birth outcome is reported as "77, Not applicable". 
<br>
<br>

#### Table 2. Preterm Birth
*Values for missing gestational age reports by US and LMP are also reported in this table. For all variables, 1 indicates "Yes" and 0 indicates "No".*
```{r, preterm birth, message = FALSE, warning = FALSE}

# N(%) without both US and LMP; (MISSING_BOTH_US_LMP)
# Distribution of GA_DIFF_DAYS; 
# N% where US is used vs. where LMP is used. (BOE_METHOD (where 1 = US and 2 = LMP))
# Histograms of GA at birth (GA_AT_BIRTH_WKS)

# a. Preterm birth (<37 weeks): Delivery prior to 37 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT37]
# b. Preterm birth (<34 weeks): Delivery prior to 34 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT34]
# c. Preterm birth (<32 weeks): Delivery prior to 32 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT32]
# d. Preterm birth (<28 weeks): Delivery prior to 28 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT28]
# e. Preterm birth severity (categorical): Late preterm (34 to <37 wks), early preterm (32 to <34 wks), very preterm (28 to <32 wks), extermely preterm (<28 weeks) [varname: PRETERMBIRTH_CAT]

mnh01_tab <- mnh01_constructed %>% 
  rowwise() %>% 
  group_by(SITE) %>% 
  summarise(
    # "Missing both US and LMP GA (MNH01)" = paste0(
    #   format(sum(MISSING_BOTH_US_LMP == 1, na.rm = TRUE), nsmall = 0, digits = 2),
    #   " (",
    #   format(round(sum(MISSING_BOTH_US_LMP == 1, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
    #   ")"),
    
    "Missing both US and LMP GA" = paste0(
      format(sum(is.na(BOE_METHOD)), nsmall = 0, digits = 2),
      " (",
      format(round(sum(is.na(BOE_METHOD))/n()*100, 2), nsmall = 0, digits = 2),
      ")"),

    "BOE = Ultrasound" = paste0(
      format(sum(BOE_METHOD == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(BOE_METHOD == 1, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    "BOE = LMP" = paste0(
      format(sum(BOE_METHOD == 2, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(BOE_METHOD == 2, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")")
  ) %>% 
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1) 


    
  
preterm_birth_tab <- preterm_birth %>% 
  rowwise() %>% 
  group_by(SITE) %>% 
  summarise(
    
    # "Preterm birth (<37 weeks), n-1" = paste0(
    #   format(sum(PRETERMBIRTH_LT37 == 1, na.rm = TRUE), nsmall = 0, digits = 2),
    #   " (",
    #   format(round(sum(PRETERMBIRTH_LT37 == 1, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #   ")"),
    # 
    # "Preterm birth (<37 weeks), n-0" = paste0(
    #       format(sum(PRETERMBIRTH_LT37 == 0, na.rm = TRUE), nsmall = 0, digits = 2),
    #       " (",
    #       format(round(sum(PRETERMBIRTH_LT37 == 0, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #       ")"),
    # 
    # "Preterm birth (<34 weeks), n-1" = paste0(
    #   format(sum(PRETERMBIRTH_LT34 == 1, na.rm = TRUE), nsmall = 0, digits = 2),
    #   " (",
    #   format(round(sum(PRETERMBIRTH_LT34 == 1, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #   ")"),
    # 
    # "Preterm birth (<34 weeks), n-0" = paste0(
    #       format(sum(PRETERMBIRTH_LT34 == 0, na.rm = TRUE), nsmall = 0, digits = 2),
    #       " (",
    #       format(round(sum(PRETERMBIRTH_LT34 == 0, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #       ")"),
    # 
    # "Preterm birth (<32 weeks), n-1" = paste0(
    #   format(sum(PRETERMBIRTH_LT32 == 1, na.rm = TRUE), nsmall = 0, digits = 2),
    #   " (",
    #   format(round(sum(PRETERMBIRTH_LT32 == 1, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #   ")"),
    # 
    # "Preterm birth (<32 weeks), n-0" = paste0(
    #       format(sum(PRETERMBIRTH_LT32 == 0, na.rm = TRUE), nsmall = 0, digits = 2),
    #       " (",
    #       format(round(sum(PRETERMBIRTH_LT32 == 0, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #       ")"),
    # 
    #   "Preterm birth (<28 weeks), n-1" = paste0(
    #   format(sum(PRETERMBIRTH_LT28 == 1, na.rm = TRUE), nsmall = 0, digits = 2),
    #   " (",
    #   format(round(sum(PRETERMBIRTH_LT28 == 1, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #   ")"),
    # 
    # "Preterm birth (<28 weeks), n-0" = paste0(
    #       format(sum(PRETERMBIRTH_LT28 == 0, na.rm = TRUE), nsmall = 0, digits = 2),
    #       " (",
    #       format(round(sum(PRETERMBIRTH_LT28 == 0, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
    #       ")"),
    
    "Preterm birth severity (categorical), n-1" = paste0(
          format(sum(PRETERMBIRTH_CAT == 11, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(PRETERMBIRTH_CAT == 11, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
    
      "Preterm birth severity (categorical), n-2" = paste0(
          format(sum(PRETERMBIRTH_CAT == 12, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(PRETERMBIRTH_CAT == 12, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
    
          "Preterm birth severity (categorical), n-3" = paste0(
          format(sum(PRETERMBIRTH_CAT == 13, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(PRETERMBIRTH_CAT == 13, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
    
          "Preterm birth severity (categorical), n-4" = paste0(
          format(sum(PRETERMBIRTH_CAT == 14, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(PRETERMBIRTH_CAT == 14, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"),
    
          "Preterm birth severity (categorical), n-5" = paste0(
          format(sum(PRETERMBIRTH_CAT == 15, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(PRETERMBIRTH_CAT == 15, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")"), 
        
    "Preterm birth severity (categorical), n-55" = paste0(
          format(sum(PRETERMBIRTH_CAT == 55, na.rm = TRUE), nsmall = 0, digits = 2),
          " (",
          format(round(sum(PRETERMBIRTH_CAT == 55, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
          ")")

    
  )  %>%
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1) 
 
bind_rows(mnh01_tab, preterm_birth_tab) %>% 
  `rownames<-` (c(
    "Missing both US and LMP GA, n (%)",
    "BOE = Ultrasound, n (%)",
    "BOE = LMP, n (%)",

    # "1",
    # "0",
    # 
    # "1 ",
    # "0 ",
    # 
    # "1  ",
    # "0  ",
    # 
    # "1   ",
    # "0   ",
    
    "Term (>= 37wks)",
    "Late preterm (34 to <37 wks)",
    "Early preterm (32 to <34 wks)",
    "Very preterm (28 to <32 wks)",
    "Extermely preterm (<28 weeks)",
    "Missing"

  )

  ) %>% 
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 16) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") %>% 
  pack_rows("MNH01 GA Data", 1, 3, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Delivery < 37wks, n (%)", 4, 5, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Delivery < 34wks, n (%)", 6, 7, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Delivery < 32wks, n (%)", 8, 9, label_row_css = "color: steelblue;")  %>% 
  # pack_rows("Delivery < 28wks, n (%)", 10, 11, label_row_css = "color: steelblue;") %>% 
  pack_rows("Preterm birth severity (categorical), n (%)", 4, 9, label_row_css = "color: steelblue;") 


```

\newpage

#### Figure 2a. Preterm Birth: Distribution of days difference between GA by US and GA by LMP reporting across sites. 
```{r preterm births fig2a}

mnh01_constructed$GA_DIFF_DAYS = abs(mnh01_constructed$GA_DIFF_DAYS)

summary_stats <- summary(mnh01_constructed$GA_DIFF_DAYS)

ggplot(data=mnh01_constructed,
       aes(x=abs(GA_DIFF_DAYS))) + 
  geom_histogram() + #binwidth = 100
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,175,25), 
                     limits = c(0,175)) + 
  ggtitle("Days difference between GA by US and GA by LMP, by Site") + 
  ylab("Count") + 
  xlab("Days difference") + 
  # geom_text(
  #   aes(x = Inf, y = Inf, label = paste(
  #     "N:", length(GA_DIFF_DAYS), "\n",
  #     "MIN:", summary_stats[1], "\n",
  #     "P5:", quantile(GA_DIFF_DAYS, 0.05, na.rm = TRUE), "\n",
  #     "MEAN:", round(mean(GA_DIFF_DAYS, na.rm = TRUE)), "\n",
  #     "MEDIAN:", median(GA_DIFF_DAYS, na.rm = TRUE), "\n",
  #     "P95:", quantile(GA_DIFF_DAYS, 0.95, na.rm = TRUE), "\n",
  #     "MAX:", summary_stats[6]
  #   )), 
  #   vjust = 1, hjust = 1, size = 3, face = "bold", color = "black"
  # ) + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60, 
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) 

#ggsave(paste0("test", ".pdf"), path = path_to_save)

```
*Figure 2a. Pakistan is not reporting LMP for any participant, which is why they have no data above.  

\newpage

#### Figure 2b. Preterm Birth: Distribution of gestational age at birth in weeks. 
```{r preterm births fig2b}

ggplot(data=preterm_birth,
       aes(x=abs(GA_AT_BIRTH_WKS))) + 
  geom_histogram() + #binwidth = 100
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(20,45,1), 
                     limits = c(20,45)) + 
  ggtitle("Gestational age at birth (weeks), by Site") + 
  ylab("Count") + 
  xlab("Gestational Age at Birth (Weeks)") + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60, 
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank())
  
```
*Figure 2b. Gestational age at birth was calculated by taking the difference between the DOB and "estimated conception date" determined by BOE.  

\newpage

### Size for Gestational Age (SGA)
**Definition:** Birth weight of an infant per INTERGROWTH standards (Per infant, including livebirths, including multiples).
<br>
<br>

**To be included in the numerator for this outcome, a participant must have:**
<br>
**1.** Reported gestational age by either LMP or Ultrasound (varnames [form]: `US_GA_WKS_AGE_FTS1-4 [MNH01]`, `US_GA_DAYS_AGE_FTS1-4 [MNH01]`, `GA_LMP_WEEKS_SCORRES [MNH01]`).
<br>
**2.** Valid date of birth (varname [form]: `DELIV_DSSTDAT_INF1-4 [MNH09]`).
<br>
**3.** Birthweight measured by PRISMA staff <72 hours following birth OR facility reported birthweight where PRISMA not available (varnames [form]: `BW_EST_FAORRES [MNH11]`, `BW_FAORRES [MNH11]`, `BW_FAORRES_REPORT [MNH11]`).
<br>
**4.** Live birth (varname [form]: `BIRTH_DSTERM_INF1-4 [MNH09]`).
<br>
<br>

**Common causes for a particpant to be marked as "Missing":**
<br>
**-** Participant is missing a reported GA by Ultrasound AND GA by LMP in MNH01.
<br>
**-** Participant is missing an enrollment ultrasound visit (`TYPE_VISIT=1`).
<br>
**-** PRISMA-measured AND Facility-reported birthweights are missing from MNH11.
<br>
**-** MNH11 forms missing for infants (i.e. infantid present in MNH09, but is missing an MNH11 form).
<br>
**-** Gestational age at birth less than 33 weeks or over 42 weeks. 
<br>
<br>

#### Table 3. Size for Gestational Age (SGA)
```{r, sga, message = FALSE, warning = FALSE}
#* 3. SGA
# a. Size for gestational age - categorical. [varname: SGA_CAT]
# b. Preterm small for gestational age: Preterm < 37 weeks AND SGA (<10th). [varname: INF_SGA_PRETERM]
# c. Preterm appropriate for gestational age: Preterm < 37 weeks AND not SGA (<10th). [varname: INF_AGA_PRETERM]
# d. Term small for gestational age: Term >=37 weeks AND SGA (<10th). [varname: INF_SGA_TERM]
# e. Term appropriate for gestational age: Term >=37 weeks AND not SGA (<10th). [varname: INF_AGA_TERM]

sga_tab <- sga %>% 
  rowwise() %>% 
  group_by(SITE) %>% 
  summarise(

    "SGA <3rd percentile" = paste0(
      format(sum(SGA_CAT == 11), nsmall = 0, digits = 2),
      " (",
      format(round(sum(SGA_CAT == 11, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")"),

    "SGA <10th percentile" = paste0(
      format(sum(SGA_CAT == 12), nsmall = 0, digits = 2),
      " (",
      format(round(sum(SGA_CAT == 12, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    "AGA 10th to <90th percentile" = paste0(
      format(sum(SGA_CAT == 13), nsmall = 0, digits = 2),
      " (",
      format(round(sum(SGA_CAT == 13, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    "LGA >= 90th percentile" = paste0(
      format(sum(SGA_CAT == 14), nsmall = 0, digits = 2),
      " (",
      format(round(sum(SGA_CAT == 14, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")"),
    
    "Missing" = paste0(
      
      format(sum(SGA_CAT == 55), nsmall = 0, digits = 2),
      " (",
      format(round(sum(SGA_CAT == 55, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
      ")"),
    
  ) %>% 
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1) 


sga_tab %>% 
  `rownames<-` (c(
    "SGA <3rd percentile",
    "SGA <10th percentile",
    "AGA 10th to <90th percentile",
    "LGA >= 90th percentile",
    "Missing"
  )

  ) %>% 
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 16) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") %>% 
  pack_rows("Size for Gestational Age (Cateogorical), n (%)", 1, 5, label_row_css = "color: steelblue;")  


```

