---
title: "Mat_GDM_tables"
author: "Fouzia Farooq"
date: '`r Sys.Date()`'
output: html_document
---

---
title: "<span style='font-size: 18px'> <span style='text-align: center'> PRISMA-Maternal-Outcomes (Issued: 2023-09-27)"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
    df_print: kable
always_allow_html: true

# knit: (function(inputFile, encoding) { 
#       out_dir <- 'output';
#       rmarkdown::render(inputFile,
#                         encoding=encoding, 
#                         output_file=file.path(dirname(inputFile), out_dir, 'PRISMA-Maternal-Outcomes-Report')) })
---

&nbsp;
&nbsp;
&nbsp;
&nbsp;


##### **Includes data from synapse last updated:** {.unlisted .unnumbered}
#####  2023-09-15 {.unlisted .unnumbered}


```{css, echo=FALSE}
.table caption {
  color: black;
  font-weight: bold;
}
```


```{r, data setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(knitr)
library(tidyverse)
library(reshape2)
library(lubridate)
library(kableExtra)
library(emo)
library(naniar)
library(dplyr)
library(RColorBrewer)
```

```{r}

df <- diabetes_df # the file that is generated in 'Mat_GDM_analysis.Rmd' -- run that first.
```
\newpage

### Gestational Diabetes 
**Definition:**
<br>
<br>

*Denominator: Enrolled women with a delivery date.
<br>
<br>

# ANC Clinical status question "Have you ever been diagnosed of diabetes" doesn't exist for Visit 5 (ANC36)
Table 1: Anemia
```{r}

# M04_DIABETES_EVER_MHOCCUR_3, M04_DIABETES_EVER_MHOCCUR_4, M04_DIABETES_EVER_MHOCCUR_5,
# M09_GEST_DIAB_MHOCCUR_6, M09_INDUCED_PROCCUR_6, M09_INDUCED_PRINDC_6,
# M19_PRIMARY_MHTERM_13, M19_LD_COMPL_MHTERM_3_13,
# 
# MEASURED VARS:
# M08_HBA1C_LBORRES_1,M06_BGLUC_POC_MMOLL_LBORRES_3,
# M08_BGLUC_PRETEST_MMOLL_LBORRES_3, M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3, M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3


# diabetes_df <- diabetes_df %>% 
#   mutate(GEST_DIAB_DIAG = case_when((M04_DIABETES_EVER_MHOCCUR_3==0 | M04_DIABETES_EVER_MHOCCUR_4==0 | M04_DIABETES_EVER_MHOCCUR_5==0) &
#                                       ((M09_GEST_DIAB_MHOCCUR_6==1 | # WAS MOTHER DIAGNOSED WITH GDM
#                                       (M09_INDUCED_PROCCUR_6==1 & M09_INDUCED_PRINDC_6==8)) |
#                                       (M19_PRIMARY_MHTERM_13==4 & M19_LD_COMPL_MHTERM_3_13)) ~ 1,
#                                     TRUE ~ as.numeric(0)))


diabetes_table <- df %>%
  rowwise() %>%
  group_by(SITE) %>%
  summarise(
    ########## MEASURED
    # confirm HbA1C at enrollment is high
    "Enrollment HbA1c: M08_HBA1C_LBORRES_1, n (%)" =
      paste0(sum(is.na(M08_HBA1C_LBORRES_1)),
             " (",
             format(round(sum(is.na(M08_HBA1C_LBORRES_1))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    # # At ANC28, POC diagnostics in fasting is >5.1
    # "ANC28 POC fasting: M06_BGLUC_POC_MMOLL_LBORRES_3, n (%)" =
    #   paste0(sum(is.na(M06_BGLUC_POC_MMOLL_LBORRES_3)),
    #          " (",
    #          format(round(sum(is.na(M06_BGLUC_POC_MMOLL_LBORRES_3))/n()*100, 2),nsmall=2, digits=3),
    #          ")"),
    
    # confirm Pre-test (fasting) OGTT is high (-1)
        "ANC28 Pretest fasting OGTT: M08_BGLUC_PRETEST_MMOLL_LBORRES_3, n (%)" =
      paste0(sum(is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3)),
             " (",
             format(round(sum(is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    # when fasting OGTT is high, then 1-hr (_2) or 2-hr (-3) should be also high 
    # 1-hr (_2) test:
            "ANC28 1-hr OGTT: M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3, n (%)" =
      paste0(sum(is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3)),
             " (",
             format(round(sum(is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    # 2-hr (_3) test:
               "ANC28 2-hr OGTT: M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3, n (%)" =
      paste0(sum(is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3)),
             " (",
             format(round(sum(is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3))/n()*100, 2),nsmall=2, digits=3),
             ")")) %>%
  
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1)
  
    
    # "Missing both at Visit 1 = NA, n (%)" =
    #   paste0(sum(is.na(M08_CBC_HB_LBORRES_1) & is.na(M06_HB_POC_LBORRES_1)),
    #          " (",
    #          format(round(sum(is.na(M08_CBC_HB_LBORRES_1) & is.na(M06_HB_POC_LBORRES_1))/n()*100, 2), nsmall=2, digits=3),
    #          ")"),
    # "anemia category high " =
    #   paste0(sum(MAT_ANEMIA_MEAS1 == "high hb >=15g/dl")),
    # " (",
    # format(round(sum(MAT_ANEMIA_MEAS1 == "high hb >=15g/dl")/n()*100,2), nsmall=2, digits=3),
    # ")")
    
```


```{r}
diabetes_table  %>% 
  `rownames<-` (c(
    "Enrollment HbA1c: M08_HBA1C_LBORRES_1, n (%)",
    "ANC28 Pretest fasting OGTT: M08_BGLUC_PRETEST_MMOLL_LBORRES_3, n (%)",
    "ANC28 1-hr OGTT: M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3, n (%)",
    "ANC28 2-hr OGTT: M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3, n (%)")) %>%
  
  
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") #

 #"Missing M08_CBC_HB_LBORRES_1 = NA, n (%)",#%>% 
 # pack_rows("PRISMA measured birthweight (categorical), n (%)", 5, 8, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Any method measured birthweight (categorical), n (%)", 9, 12, label_row_css = "color: steelblue;") 
```

# DIAGNOSED
```{r}
# diabetes_df <- diabetes_df %>% 
#   mutate(GEST_DIAB_DIAG = case_when((M04_DIABETES_EVER_MHOCCUR_3==0 | M04_DIABETES_EVER_MHOCCUR_4==0 | M04_DIABETES_EVER_MHOCCUR_5==0) &
#                                       ((M09_GEST_DIAB_MHOCCUR_6==1 | # WAS MOTHER DIAGNOSED WITH GDM
#                                       (M09_INDUCED_PROCCUR_6==1 & M09_INDUCED_PRINDC_6==8)) |
#                                       (M19_PRIMARY_MHTERM_13==4 & M19_LD_COMPL_MHTERM_3_13)) ~ 1,
#                                     TRUE ~ as.numeric(0)))


diabetes_table <- df %>%
  rowwise() %>%
  group_by(SITE) %>%
  summarise(
    ########## DIAGNOSED 
    # 
    "ANC28 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_3, n (%)" =
      paste0(sum(is.na(M04_DIABETES_EVER_MHOCCUR_3)),
             " (",
             format(round(sum(is.na(M04_DIABETES_EVER_MHOCCUR_3))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    "ANC32 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_4, n (%)" =
      paste0(sum(is.na(M04_DIABETES_EVER_MHOCCUR_4)),
             " (",
             format(round(sum(is.na(M04_DIABETES_EVER_MHOCCUR_4))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    "ANC36 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_5, n (%)" =
      paste0(sum(is.na(M04_DIABETES_EVER_MHOCCUR_5)),
             " (",
             format(round(sum(is.na(M04_DIABETES_EVER_MHOCCUR_5))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    "L&D Induced: M09_INDUCED_PROCCUR_6, n (%)" =
      paste0(sum(is.na(M09_INDUCED_PROCCUR_6)),
             " (",
             format(round(sum(is.na(M09_INDUCED_PROCCUR_6))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    
    "L&D Induced: M09_INDUCED_PRINDC_6, n (%)" =
      paste0(sum(is.na(M09_INDUCED_PRINDC_6)),
             " (",
             format(round(sum(is.na(M09_INDUCED_PRINDC_6))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    
    "Hospitalization: M19_PRIMARY_MHTERM_13, n (%)" =
      paste0(sum(is.na(M19_PRIMARY_MHTERM_13)),
             " (",
             format(round(sum(is.na(M19_PRIMARY_MHTERM_13))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    "Hospitalization: M19_LD_COMPL_MHTERM_3_13, n (%)" =
      paste0(sum(is.na(M19_LD_COMPL_MHTERM_3_13)),
             " (",
             format(round(sum(is.na(M19_LD_COMPL_MHTERM_3_13))/n()*100, 2),nsmall=2, digits=3),
             ")"))%>%
  
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1)
    
```

```{r}
diabetes_table  %>% 
  `rownames<-` (c(
    "ANC28 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_3, n (%)",
    "ANC32 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_4, n (%)",
    "ANC36 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_5, n (%)",
    "L&D Induced: M09_INDUCED_PROCCUR_6, n (%)",
    "L&D Induced: M09_INDUCED_PRINDC_6, n (%)",
    "Hospitalization: M19_PRIMARY_MHTERM_13, n (%)",
    "Hospitalization: M19_LD_COMPL_MHTERM_3_13, n (%)")) %>%
  
  
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") #

 #"Missing M08_CBC_HB_LBORRES_1 = NA, n (%)",#%>% 
 # pack_rows("PRISMA measured birthweight (categorical), n (%)", 5, 8, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Any method measured birthweight (categorical), n (%)", 9, 12, label_row_css = "color: steelblue;") 
```

    