---
title: "Mat_anemia"
author: "Fouzia Farooq"
date: "`r Sys.Date()`"
output: html_document
---

---
title: "<span style='font-size: 18px'> <span style='text-align: center'> PRISMA-Maternal-Outcomes (Issued: 2023-09-27)"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
    df_print: kable
always_allow_html: true

# knit: (function(inputFile, encoding) { 
#       out_dir <- 'output';
#       rmarkdown::render(inputFile,
#                         encoding=encoding, 
#                         output_file=file.path(dirname(inputFile), out_dir, 'PRISMA-Maternal-Outcomes-Report')) })
---

&nbsp;
&nbsp;
&nbsp;
&nbsp;


##### **Includes data from synapse last updated:** {.unlisted .unnumbered}
#####  2023-09-15 {.unlisted .unnumbered}


```{css, echo=FALSE}
.table caption {
  color: black;
  font-weight: bold;
}
```


```{r, data setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(knitr)
library(tidyverse)
library(reshape2)
library(lubridate)
library(kableExtra)
library(emo)
library(naniar)
library(dplyr)
library(RColorBrewer)
```

```{r}
# df <- read.csv('data_out/mat_anemia_analysis.csv')
df <- anemia_df # the file that is generated in 'Mat_anemia_analysis.Rmd'
```
\newpage

### Maternal Anemia (ANC, L&D, PNC-0, PNC-1, PNC-4)
**Definition:** Hemoglobin (g/dl) below defined cutoff among women who had a delivery date
<br>
<br>

*Denominator: Enrolled women with a delivery date.
<br>
<br>

Table 1: Anemia
```{r}
anemia_table <- df %>%
  rowwise() %>%
  group_by(SITE) %>%
  summarise(
    "Missing M08_CBC_HB_LBORRES_1 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_1)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_1))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    "Missing M06_HB_POC_LBORRES_1 = NA, n (%)" =
      paste0(sum(is.na(M06_HB_POC_LBORRES_1)),
             " (",
             format(round(sum(is.na(M06_HB_POC_LBORRES_1))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    "Missing both at Visit 1 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_1) & is.na(M06_HB_POC_LBORRES_1)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_1) & is.na(M06_HB_POC_LBORRES_1))/n()*100, 2), nsmall=2, digits=3),
             ")"),
    
    # VISIT 2
    "Missing M08_CBC_HB_LBORRES_2 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_2)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_2))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    "Missing M06_HB_POC_LBORRES_2 = NA, n (%)" =
      paste0(sum(is.na(M06_HB_POC_LBORRES_2)),
             " (",
             format(round(sum(is.na(M06_HB_POC_LBORRES_2))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
    "Missing both at Visit 2 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_2) & is.na(M06_HB_POC_LBORRES_2)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_2) & is.na(M06_HB_POC_LBORRES_2))/n()*100, 2), nsmall=2, digits=3),
             ")"),
    
    # VISIT 3
    "Missing M08_CBC_HB_LBORRES_3 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_3)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_3))/n()*100, 2),nsmall=2, digits=3),
             ")") ,
    
    "Missing M06_HB_POC_LBORRES_3 = NA, n (%)" =
      paste0(sum(is.na(M06_HB_POC_LBORRES_3)),
             " (",
             format(round(sum(is.na(M06_HB_POC_LBORRES_3))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
        "Missing both at Visit 3 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_3) & is.na(M06_HB_POC_LBORRES_3)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_3) & is.na(M06_HB_POC_LBORRES_3))/n()*100, 2), nsmall=2, digits=3),
             ")"),
    
    
    # VISIT 4
    "Missing M08_CBC_HB_LBORRES_4 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_4)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_4))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    "Missing M06_HB_POC_LBORRES_4 = NA, n (%)" =
      paste0(sum(is.na(M06_HB_POC_LBORRES_4)),
             " (",
             format(round(sum(is.na(M06_HB_POC_LBORRES_4))/n()*100, 2),nsmall=2, digits=3),
             ")"),
        "Missing both at Visit 4 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_4) & is.na(M06_HB_POC_LBORRES_4)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_4) & is.na(M06_HB_POC_LBORRES_4))/n()*100, 2), nsmall=2, digits=3),
             ")"),
    
    # VISIT 5
    "Missing M08_CBC_HB_LBORRES_5 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_5)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_5))/n()*100, 2),nsmall=2, digits=3),
             ")") ,
    "Missing M06_HB_POC_LBORRES_5 = NA, n (%)" =
      paste0(sum(is.na(M06_HB_POC_LBORRES_5)),
             " (",
             format(round(sum(is.na(M06_HB_POC_LBORRES_5))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
        "Missing both at Visit 5 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_5) & is.na(M06_HB_POC_LBORRES_5)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_5) & is.na(M06_HB_POC_LBORRES_5))/n()*100, 2), nsmall=2, digits=3),
             ")"),
    
    # IPC - VISIT 6
    "Missing M08_CBC_HB_LBORRES_6 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_6)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_6))/n()*100, 2),nsmall=2, digits=3),
             ")"),
        
    "Missing M06_HB_POC_LBORRES_6 = NA, n (%)" =
      paste0(sum(is.na(M06_HB_POC_LBORRES_6)),
             " (",
             format(round(sum(is.na(M06_HB_POC_LBORRES_6))/n()*100, 2),nsmall=2, digits=3),
             ")"),
    
        "Missing both at Visit 6 = NA, n (%)" =
      paste0(sum(is.na(M08_CBC_HB_LBORRES_6) & is.na(M06_HB_POC_LBORRES_6)),
             " (",
             format(round(sum(is.na(M08_CBC_HB_LBORRES_6) & is.na(M06_HB_POC_LBORRES_6))/n()*100, 2), nsmall=2, digits=3),
             ")"))%>%
  
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1)
    

    
    # # VISIT 7, 8,9 - ONLY HAVE POC
    # # VISIT 7
    # "Missing M06_HB_POC_LBORRES_7 = NA, n (%)" =
    #   paste0(sum(is.na(M06_HB_POC_LBORRES_7)),
    #          " (",
    #          format(round(sum(is.na(M06_HB_POC_LBORRES_7))/n()*100, 2),nsmall=2, digits=3),
    #          ")"),
    # # VISIT 8
    # "Missing M06_HB_POC_LBORRES_8 = NA, n (%)" =
    #   paste0(sum(is.na(M06_HB_POC_LBORRES_8)),
    #          " (",
    #          format(round(sum(is.na(M06_HB_POC_LBORRES_8))/n()*100, 2),nsmall=2, digits=3),
    #          ")") ,
    # # VISIT 9
    # "Missing M06_HB_POC_LBORRES_9 = NA, n (%)" =
    #   paste0(sum(is.na(M06_HB_POC_LBORRES_9)),
    #          " (",
    #          format(round(sum(is.na(M06_HB_POC_LBORRES_9))/n()*100, 2),nsmall=2, digits=3),
    #          ")"),
```
 
```{r}
anemia_table  %>% 
  `rownames<-` (c(
    "Missing M08_CBC_HB_LBORRES_1 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_1 = NA, n (%)",
    "Missing both at Visit 1 = NA, n(%)",
    "Missing M08_CBC_HB_LBORRES_2 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_2 = NA, n (%)",
    "Missing both at Visit 2 = NA, n(%)",
    "Missing M08_CBC_HB_LBORRES_3 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_3 = NA, n (%)",
    "Missing both at Visit 3 = NA, n(%)",
    "Missing M08_CBC_HB_LBORRES_4 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_4 = NA, n (%)",
    "Missing both at Visit 4 = NA, n(%)",
    "Missing M08_CBC_HB_LBORRES_5 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_5 = NA, n (%)",
    "Missing both at Visit 5 = NA, n(%)",
    "Missing M08_CBC_HB_LBORRES_6 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_6 = NA, n (%)",
    "Missing both at Visit 6 = NA, n(%)")) %>%
  
  
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") #

 #"Missing M08_CBC_HB_LBORRES_1 = NA, n (%)",#%>% 
 # pack_rows("PRISMA measured birthweight (categorical), n (%)", 5, 8, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Any method measured birthweight (categorical), n (%)", 9, 12, label_row_css = "color: steelblue;") 
```


 
```{r}




  # t() %>% as.data.frame() %>% 
  # `colnames<-`(c(.[1,])) %>% 
  # slice(-1) 

```

```{r}
anemia_table  %>% 
  `rownames<-` (c(
    "Missing M08_CBC_HB_LBORRES_1 = NA, n (%)", 
    "Missing M08_CBC_HB_LBORRES_2 = NA, n (%)", 
    "Missing M08_CBC_HB_LBORRES_3 = NA, n (%)",
    "Missing M08_CBC_HB_LBORRES_4 = NA, n (%)",
    "Missing M08_CBC_HB_LBORRES_5 = NA, n (%)",
    "Missing M08_CBC_HB_LBORRES_6 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_1 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_2 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_3 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_4 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_5 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_6 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_7 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_8 = NA, n (%)",
    "Missing M06_HB_POC_LBORRES_9 = NA, n (%)")
  ) %>% 
  
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") #

 #"Missing M08_CBC_HB_LBORRES_1 = NA, n (%)",#%>% 
 # pack_rows("PRISMA measured birthweight (categorical), n (%)", 5, 8, label_row_css = "color: steelblue;") %>% 
  # pack_rows("Any method measured birthweight (categorical), n (%)", 9, 12, label_row_css = "color: steelblue;") 
```

