---
title: "<span style='font-size: 18px'> <span style='text-align: center'> PRISMA-Maternal-Outcomes (Issued: 2023-09-26)"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
    df_print: kable
always_allow_html: true

knit: (function(inputFile, encoding) { 
      out_dir <- 'output';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), 'data_out' , 'PRISMA-Maternal-Outcomes-Report')) })
---

&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{css, echo=FALSE}
.table caption {
  color: black;
  font-weight: bold;
}
```


```{r, data setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

#*****************************************************************************
#* PRISMA Maternal Outcomes -- TABLES 
#* Drafted: 26 September 2023, Fouzia Farooq

#*****************************************************************************
library(knitr)
library(tidyverse)
library(reshape2)
library(lubridate)
# library(kableExtra)
library(emo)
library(naniar)
library(dplyr)
library(RColorBrewer)

UploadDate <- "2023-09-15"
path_to_data <-  'D:/Users/fouziafarooq/Documents/PRISMA_constructed-outcomes/data_out/'# - for AWS data
path_to_save <-  'D:/Users/fouziafarooq/Documents/PRISMA_constructed-outcomes/data_out/'# - for AWS data

preeclampsia <- read.csv(paste0(path_to_data, "preeclampsia.csv"))


#mnh01_constructed <- read.csv(paste0(path_to_data, "mnh01_constructed.csv"))

```

#### Table 2. chronic hypertension
*Values for missing gestational age reports by US and LMP are also reported in this table. For all variables, 1 indicates "Yes" and 0 indicates "No".*
```{r, preterm birth, message = FALSE, warning = FALSE}

# N(%) without both US and LMP; (MISSING_BOTH_US_LMP)
# Distribution of GA_DIFF_DAYS; 
# N% where US is used vs. where LMP is used. (BOE_METHOD (where 1 = US and 2 = LMP))
# Histograms of GA at birth (GA_AT_BIRTH_WKS)

# a. Preterm birth (<37 weeks): Delivery prior to 37 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT37]
# b. Preterm birth (<34 weeks): Delivery prior to 34 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT34]
# c. Preterm birth (<32 weeks): Delivery prior to 32 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT32]
# d. Preterm birth (<28 weeks): Delivery prior to 28 completed weeks of gestation (live or stillbirth). [varname: PRETERMBIRTH_LT28]
# e. Preterm birth severity (categorical): Late preterm (34 to <37 wks), early preterm (32 to <34 wks), very preterm (28 to <32 wks), extermely preterm (<28 weeks) [varname: PRETERMBIRTH_CAT]

mnh01_tab <- preeclampsia %>% 
  rowwise() %>% 
  group_by(SITE) %>% 
  summarise(
    # "Missing both US and LMP GA (MNH01)" = paste0(
    #   format(sum(MISSING_BOTH_US_LMP == 1, na.rm = TRUE), nsmall = 0, digits = 2),
    #   " (",
    #   format(round(sum(MISSING_BOTH_US_LMP == 1, na.rm = TRUE)/n()*100, 2), nsmall = 0, digits = 2),
    #   ")"),
    
    "Missing BP_SYS from MNH06" = paste0(
      format(sum(is.na(M06_BP_SYS_VSORRES_1_1)), nsmall = 0, digits = 2),
      " (",
      format(round(sum(is.na(M06_BP_SYS_VSORRES_1_1))/n()*100, 2), nsmall = 0, digits = 2),
      ")")
    
  ) %>% 
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1) 


#     
#   
# preterm_birth_tab <- preterm_birth %>% 
#   rowwise() %>% 
#   group_by(SITE) %>% 
#   summarise(
#     
# 
#     "Chronic Hypertension (categorical), n-1" = paste0(
#           format(sum(CHRON_HYPER==1, na.rm = TRUE), nsmall = 0, digits = 2),
#           " (",
#           format(round(sum(CHRON_HYPER==1, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
#           ")"),
#     
#       "Preterm birth severity (categorical), n-2" = paste0(
#           format(sum(PRETERMBIRTH_CAT == 12, na.rm = TRUE), nsmall = 0, digits = 2),
#           " (",
#           format(round(sum(PRETERMBIRTH_CAT == 12, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
#           ")"),
#     
#           "Preterm birth severity (categorical), n-3" = paste0(
#           format(sum(PRETERMBIRTH_CAT == 13, na.rm = TRUE), nsmall = 0, digits = 2),
#           " (",
#           format(round(sum(PRETERMBIRTH_CAT == 13, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
#           ")"),
#     
#           "Preterm birth severity (categorical), n-4" = paste0(
#           format(sum(PRETERMBIRTH_CAT == 14, na.rm = TRUE), nsmall = 0, digits = 2),
#           " (",
#           format(round(sum(PRETERMBIRTH_CAT == 14, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
#           ")"),
#     
#           "Preterm birth severity (categorical), n-5" = paste0(
#           format(sum(PRETERMBIRTH_CAT == 15, na.rm = TRUE), nsmall = 0, digits = 2),
#           " (",
#           format(round(sum(PRETERMBIRTH_CAT == 15, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
#           ")"), 
#         
#     "Preterm birth severity (categorical), n-55" = paste0(
#           format(sum(PRETERMBIRTH_CAT == 55, na.rm = TRUE), nsmall = 0, digits = 2),
#           " (",
#           format(round(sum(PRETERMBIRTH_CAT == 55, na.rm = TRUE)/sum(BIRTH_OUTCOME==1, na.rm = TRUE)*100, 2), nsmall = 0, digits = 2),
#           ")")
# 
#     
#   )  %>%
#   t() %>% as.data.frame() %>% 
#   `colnames<-`(c(.[1,])) %>% 
#   slice(-1) 
#  
# bind_rows(mnh01_tab, preterm_birth_tab) %>% 
#   `rownames<-` (c(
#     "Missing both US and LMP GA, n (%)",
#     "BOE = Ultrasound, n (%)",
#     "BOE = LMP, n (%)",
# 
#     # "1",
#     # "0",
#     # 
#     # "1 ",
#     # "0 ",
#     # 
#     # "1  ",
#     # "0  ",
#     # 
#     # "1   ",
#     # "0   ",
#     
#     "Term (>= 37wks)",
#     "Late preterm (34 to <37 wks)",
#     "Early preterm (32 to <34 wks)",
#     "Very preterm (28 to <32 wks)",
#     "Extermely preterm (<28 weeks)",
#     "Missing"
# 
#   )
# 
#   ) %>% 
#   mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
#   kbl(caption = "", booktabs = TRUE) %>%
#   kable_paper(bootstrap_options = "striped", 
#               full_width = T, html_font = "Cambria", position = "left",
#               latex_options = c("repeat_header", "HOLD_position")) %>% 
#   kable_styling(font_size = 16) %>%
#   row_spec(0, extra_css = "border-bottom: 0px white;") %>% 
#   pack_rows("MNH01 GA Data", 1, 3, label_row_css = "color: steelblue;") %>% 
#   # pack_rows("Delivery < 37wks, n (%)", 4, 5, label_row_css = "color: steelblue;") %>% 
#   # pack_rows("Delivery < 34wks, n (%)", 6, 7, label_row_css = "color: steelblue;") %>% 
#   # pack_rows("Delivery < 32wks, n (%)", 8, 9, label_row_css = "color: steelblue;")  %>% 
#   # pack_rows("Delivery < 28wks, n (%)", 10, 11, label_row_css = "color: steelblue;") %>% 
#   pack_rows("Preterm birth severity (categorical), n (%)", 4, 9, label_row_css = "color: steelblue;") 
# 
# 
# ```
# 
# \newpage
# 
# #### Figure 1a. Preterm Birth: Distribution of days difference between GA by US and GA by LMP reporting across sites. 
# ```{r preterm births fig2a}
# 
# mnh01_constructed$GA_DIFF_DAYS = abs(mnh01_constructed$GA_DIFF_DAYS)
# 
# summary_stats <- summary(mnh01_constructed$GA_DIFF_DAYS)
# 
# ggplot(data=mnh01_constructed,
#        aes(x=abs(GA_DIFF_DAYS))) + 
#   geom_histogram() + #binwidth = 100
#   facet_grid(vars(SITE), scales = "free") +
#   scale_x_continuous(breaks = seq(0,175,25), 
#                      limits = c(0,175)) + 
#   ggtitle("Days difference between GA by US and GA by LMP, by Site") + 
#   ylab("Count") + 
#   xlab("Days difference") + 
#   # geom_text(
#   #   aes(x = Inf, y = Inf, label = paste(
#   #     "N:", length(GA_DIFF_DAYS), "\n",
#   #     "MIN:", summary_stats[1], "\n",
#   #     "P5:", quantile(GA_DIFF_DAYS, 0.05, na.rm = TRUE), "\n",
#   #     "MEAN:", round(mean(GA_DIFF_DAYS, na.rm = TRUE)), "\n",
#   #     "MEDIAN:", median(GA_DIFF_DAYS, na.rm = TRUE), "\n",
#   #     "P95:", quantile(GA_DIFF_DAYS, 0.95, na.rm = TRUE), "\n",
#   #     "MAX:", summary_stats[6]
#   #   )), 
#   #   vjust = 1, hjust = 1, size = 3, face = "bold", color = "black"
#   # ) + 
#   theme_bw() +
#   theme(strip.background=element_rect(fill="white")) + #color
#   theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60, 
#         legend.position="bottom",
#         legend.title = element_blank(),
#         panel.grid.minor = element_blank()) 
# 
# #ggsave(paste0("test", ".pdf"), path = path_to_save)
# 
# ```
#  
# 
# \newpage
# 
# #### Figure 1a. Distribution of BP at X timepoint. 
# ```{r preterm births fig2b}
# 
# ggplot(data=preterm_birth,
#        aes(x=abs(GA_AT_BIRTH_WKS))) + 
#   geom_histogram() + #binwidth = 100
#   facet_grid(vars(SITE), scales = "free") +
#   scale_x_continuous(breaks = seq(20,45,1), 
#                      limits = c(20,45)) + 
#   ggtitle("Gestational age at birth (weeks), by Site") + 
#   ylab("Count") + 
#   xlab("Gestational Age at Birth (Weeks)") + 
#   theme_bw() +
#   theme(strip.background=element_rect(fill="white")) + #color
#   theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60, 
#         legend.position="bottom",
#         legend.title = element_blank(),
#         panel.grid.minor = element_blank())
#   
```

\newpage