---
title: "Mat_anemia_analysis"
author: "Fouzia Farooq"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(stringr)
# library(ThemePark)
library(purrr)
library(lubridate)
library(readr)
library(tidyr)
library(haven)
library(tableone)
library(kableExtra)

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# READ IN FILES:
```{r}
anemia_df <- read.csv('../data_out/mat_anemia_foranalysis.csv')
window_subset_df <- read.csv('../data_out/window_subset_df.csv')
```

# MERGE IN THE TWO SUBSETS
```{r}
anemia_df <- left_join(anemia_df, window_subset_df, 
                         by = c("MOMID", "PREGID", "SITE"))
```


# Convert "1907-07-07" to NA:
# CATEGORICAL: 
# ---- 77, Not applicable 
# ---- 55, Missing 
# ---- 66, Refused to answer
# ---- 99, Don't know

# CONTINUOUS:
# ---- -7, Not applicable 
# ---- -5, Missing 
# ---- -6, Refused to answer
# ---- -9, Don't know
# DATE: 
# ---- 07-07-1907, Not applicable 
# ---- 05-05-1905, Missing 
# ---- 06-06-1906, Refused to answer
# ---- 09-09-1909, Don't know

# TIME: 
# ---- 77:77, Not applicable 
# ---- 55:55, Missing 
# ---- 66:66, Refused to answer
# ---- 99:99, Don't know
```{r echo=FALSE}
CONVERT_NA <- TRUE
if(CONVERT_NA ==TRUE){
  
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d=="1907-07-07", NA, d)
    })
  
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-7, NA, d)
    })
  
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==77, NA, d)
    })
  
  # -5 IS MISSING FOR CONTINOUS
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-5, NA, d)
    })
  
  # 55 IS MISSING FOR CATEGORICAL
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d==55, NA, d) 
    })
  
  # 55:55 IS MISSING FOR TIME
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d=='55:55', NA, d)
    })
  
}
```



Create anemia levels for each ANC Visit
WHO Hb thresholds g/dl:
Mild: 10.0-10.9
Moderate: 7.0-9.9
Severe: <7
Normal: >=11.0
Excess Hb: >13
# ANC VISIT 1 - ENROLLMENT
```{r}
anemia_df <- anemia_df %>% filter(DELIVERED_FF==1) # SUBSET TO WOMEN WHO HAD A DELIVERY

anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS1 = case_when((!is.na(M08_CBC_HB_LBORRES_1) & 
                                        M08_CBC_HB_LBORRES_1>=10 & M08_CBC_HB_LBORRES_1<11) ~ "mild",
                                      (is.na(M08_CBC_HB_LBORRES_1) & !is.na(M06_HB_POC_LBORRES_1) & 
                                        M06_HB_POC_LBORRES_1>=10 & M06_HB_POC_LBORRES_1<11) ~ "mild",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_1) & 
                                        M08_CBC_HB_LBORRES_1>=7 & M08_CBC_HB_LBORRES_1<10) ~ "moderate",
                                      (is.na(M08_CBC_HB_LBORRES_1) & !is.na(M06_HB_POC_LBORRES_1) & 
                                        M06_HB_POC_LBORRES_1>=7 & M06_HB_POC_LBORRES_1<10) ~ "moderate",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_1) & 
                                        M08_CBC_HB_LBORRES_1>=0 & M08_CBC_HB_LBORRES_1<7) ~ "severe",
                                      (is.na(M08_CBC_HB_LBORRES_1) & !is.na(M06_HB_POC_LBORRES_1) & 
                                        M06_HB_POC_LBORRES_1>=0 & M06_HB_POC_LBORRES_1<7) ~ "severe",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_1) & 
                                        M08_CBC_HB_LBORRES_1>=11 & M08_CBC_HB_LBORRES_1<=13) ~ "normal",
                                      (is.na(M08_CBC_HB_LBORRES_1) & !is.na(M06_HB_POC_LBORRES_1) & 
                                        M06_HB_POC_LBORRES_1>=11 & M06_HB_POC_LBORRES_1<=13) ~ "normal",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_1) & 
                                        M08_CBC_HB_LBORRES_1>13 & M08_CBC_HB_LBORRES_1<15) ~ "high hb 13-<15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_1) & !is.na(M06_HB_POC_LBORRES_1) & 
                                        M06_HB_POC_LBORRES_1>13 & M06_HB_POC_LBORRES_1<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_1) & M08_CBC_HB_LBORRES_1>=15)  ~ "high hb >=15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_1) & !is.na(M06_HB_POC_LBORRES_1) & 
                                      M06_HB_POC_LBORRES_1>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))



temp.df <- anemia_df %>% 
  select(MOMID, SITE, MAT_ANEMIA_MEAS1, M08_CBC_HB_LBORRES_1, M06_HB_POC_LBORRES_1)

sum(anemia_df$M08_CBC_HB_LBORRES_1 %in% c(-5, -7))

table(MAT_ANEMIA_MEAS1 = anemia_df$MAT_ANEMIA_MEAS1, useNA = "always", SITE = anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS1, useNA = "always", anemia_df$SITE), margin=2)*100,2) 

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, M08_CBC_HB_LBORRES_1, M06_HB_POC_LBORRES_1, MAT_ANEMIA_MEAS1) %>% filter(SITE=='Ghana')

temp.df <- temp.df %>% 
  mutate(MISSING_BOTH_ANC1 =  case_when(is.na(M08_CBC_HB_LBORRES_1) & is.na(M06_HB_POC_LBORRES_1) ~ 1, 
                                        TRUE ~ as.numeric(0)))

anemia_df <- anemia_df %>%
  mutate(HIGH_HB_gt15 = case_when(MAT_ANEMIA_MEAS1=="high hb >=15g/dl" ~ 1, TRUE ~0))
```

# VISIT 2
```{r}
# ANEMIA ANC 20 - VISIT 2

anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS2 = case_when((!is.na(M08_CBC_HB_LBORRES_2) & 
                                        M08_CBC_HB_LBORRES_2>=10 & M08_CBC_HB_LBORRES_2<11) ~ "mild",
                                      (is.na(M08_CBC_HB_LBORRES_2) & !is.na(M06_HB_POC_LBORRES_2) & 
                                        M06_HB_POC_LBORRES_2>=10 & M06_HB_POC_LBORRES_2<11) ~ "mild",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_2) & 
                                        M08_CBC_HB_LBORRES_2>=7 & M08_CBC_HB_LBORRES_2<10) ~ "moderate",
                                      (is.na(M08_CBC_HB_LBORRES_2) & !is.na(M06_HB_POC_LBORRES_2) & 
                                        M06_HB_POC_LBORRES_2>=7 & M06_HB_POC_LBORRES_2<10) ~ "moderate",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_2) & 
                                        M08_CBC_HB_LBORRES_2>=0 & M08_CBC_HB_LBORRES_2<7) ~ "severe",
                                      (is.na(M08_CBC_HB_LBORRES_2) & !is.na(M06_HB_POC_LBORRES_2) & 
                                        M06_HB_POC_LBORRES_2>=0 & M06_HB_POC_LBORRES_2<7) ~ "severe",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_2) & 
                                        M08_CBC_HB_LBORRES_2>=11 & M08_CBC_HB_LBORRES_2<=13) ~ "normal",
                                      (is.na(M08_CBC_HB_LBORRES_2) & !is.na(M06_HB_POC_LBORRES_2) & 
                                        M06_HB_POC_LBORRES_2>=11 & M06_HB_POC_LBORRES_2<=13) ~ "normal",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_2) & 
                                        M08_CBC_HB_LBORRES_2>13 & M08_CBC_HB_LBORRES_2<15) ~ "high hb 13-<15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_2) & !is.na(M06_HB_POC_LBORRES_2) & 
                                        M06_HB_POC_LBORRES_2>13 & M06_HB_POC_LBORRES_2<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_2) & M08_CBC_HB_LBORRES_2>=15)  ~ "high hb >=15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_2) & !is.na(M06_HB_POC_LBORRES_2) & 
                                      M06_HB_POC_LBORRES_2>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, M08_CBC_HB_LBORRES_2, M06_HB_POC_LBORRES_2, MAT_ANEMIA_MEAS2)
# write.csv(temp.df, 'data_out/temp.df.csv')

table(anemia_df$MAT_ANEMIA_MEAS2, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS2, useNA = "always", anemia_df$SITE), margin=2)*100,2)  

```

# VISIT 3
```{r}
  #SETTING UP VISIT 3 - ANC28.
# 3RD trimester

anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS3 = case_when((!is.na(M08_CBC_HB_LBORRES_3) & 
                                        M08_CBC_HB_LBORRES_3>=10 & M08_CBC_HB_LBORRES_3<11) ~ "mild",
                                      (is.na(M08_CBC_HB_LBORRES_3) & !is.na(M06_HB_POC_LBORRES_3) & 
                                        M06_HB_POC_LBORRES_3>=10 & M06_HB_POC_LBORRES_3<11) ~ "mild",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_3) & 
                                        M08_CBC_HB_LBORRES_3>=7 & M08_CBC_HB_LBORRES_3<10) ~ "moderate",
                                      (is.na(M08_CBC_HB_LBORRES_3) & !is.na(M06_HB_POC_LBORRES_3) & 
                                        M06_HB_POC_LBORRES_3>=7 & M06_HB_POC_LBORRES_3<10) ~ "moderate",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_3) & 
                                        M08_CBC_HB_LBORRES_3>=0 & M08_CBC_HB_LBORRES_3<7) ~ "severe",
                                      (is.na(M08_CBC_HB_LBORRES_3) & !is.na(M06_HB_POC_LBORRES_3) & 
                                        M06_HB_POC_LBORRES_3>=0 & M06_HB_POC_LBORRES_3<7) ~ "severe",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_3) & 
                                        M08_CBC_HB_LBORRES_3>=11 & M08_CBC_HB_LBORRES_3<=13) ~ "normal",
                                      (is.na(M08_CBC_HB_LBORRES_3) & !is.na(M06_HB_POC_LBORRES_3) & 
                                        M06_HB_POC_LBORRES_3>=11 & M06_HB_POC_LBORRES_3<=13) ~ "normal",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_3) & 
                                        M08_CBC_HB_LBORRES_3>13 & M08_CBC_HB_LBORRES_3<15) ~ "high hb 13-<15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_3) & !is.na(M06_HB_POC_LBORRES_3) & 
                                        M06_HB_POC_LBORRES_3>13 & M06_HB_POC_LBORRES_3<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_3) & M08_CBC_HB_LBORRES_3>=15)  ~ "high hb >=15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_3) & !is.na(M06_HB_POC_LBORRES_3) & 
                                      M06_HB_POC_LBORRES_3>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS3, M08_CBC_HB_LBORRES_3, M06_HB_POC_LBORRES_3)

table(anemia_df$MAT_ANEMIA_MEAS3, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS3, useNA = "always", anemia_df$SITE), margin=2)*100,2)

```

# VISIT 4
```{r}
  #SETTING UP VISIT 4 - ANC32.
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS4 = case_when((!is.na(M08_CBC_HB_LBORRES_4) & 
                                        M08_CBC_HB_LBORRES_4>=10 & M08_CBC_HB_LBORRES_4<11) ~ "mild",
                                      (is.na(M08_CBC_HB_LBORRES_4) & !is.na(M06_HB_POC_LBORRES_4) & 
                                        M06_HB_POC_LBORRES_4>=10 & M06_HB_POC_LBORRES_4<11) ~ "mild",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_4) & 
                                        M08_CBC_HB_LBORRES_4>=7 & M08_CBC_HB_LBORRES_4<10) ~ "moderate",
                                      (is.na(M08_CBC_HB_LBORRES_4) & !is.na(M06_HB_POC_LBORRES_4) & 
                                        M06_HB_POC_LBORRES_4>=7 & M06_HB_POC_LBORRES_4<10) ~ "moderate",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_4) & 
                                        M08_CBC_HB_LBORRES_4>=0 & M08_CBC_HB_LBORRES_4<7) ~ "severe",
                                      (is.na(M08_CBC_HB_LBORRES_4) & !is.na(M06_HB_POC_LBORRES_4) & 
                                        M06_HB_POC_LBORRES_4>=0 & M06_HB_POC_LBORRES_4<7) ~ "severe",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_4) & 
                                        M08_CBC_HB_LBORRES_4>=11 & M08_CBC_HB_LBORRES_4<=13) ~ "normal",
                                      (is.na(M08_CBC_HB_LBORRES_4) & !is.na(M06_HB_POC_LBORRES_4) & 
                                        M06_HB_POC_LBORRES_4>=11 & M06_HB_POC_LBORRES_4<=13) ~ "normal",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_4) & 
                                        M08_CBC_HB_LBORRES_4>13 & M08_CBC_HB_LBORRES_4<15) ~ "high hb 13-<15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_4) & !is.na(M06_HB_POC_LBORRES_4) & 
                                        M06_HB_POC_LBORRES_4>13 & M06_HB_POC_LBORRES_4<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_4) & M08_CBC_HB_LBORRES_4>=15)  ~ "high hb >=15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_4) & !is.na(M06_HB_POC_LBORRES_4) & 
                                      M06_HB_POC_LBORRES_4>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS4, M08_CBC_HB_LBORRES_4, M06_HB_POC_LBORRES_4)

table(anemia_df$MAT_ANEMIA_MEAS4, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS4, useNA = "always", anemia_df$SITE), margin=2)*100,2)
```

# VISIT 5
```{r}
  #SETTING UP VISIT 5 - ANC36.

anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS5 = case_when((!is.na(M08_CBC_HB_LBORRES_5) & 
                                        M08_CBC_HB_LBORRES_5>=10 & M08_CBC_HB_LBORRES_5<11) ~ "mild",
                                      (is.na(M08_CBC_HB_LBORRES_5) & !is.na(M06_HB_POC_LBORRES_5) & 
                                        M06_HB_POC_LBORRES_5>=10 & M06_HB_POC_LBORRES_5<11) ~ "mild",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_5) & 
                                        M08_CBC_HB_LBORRES_5>=7 & M08_CBC_HB_LBORRES_5<10) ~ "moderate",
                                      (is.na(M08_CBC_HB_LBORRES_5) & !is.na(M06_HB_POC_LBORRES_5) & 
                                        M06_HB_POC_LBORRES_5>=7 & M06_HB_POC_LBORRES_5<10) ~ "moderate",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_5) & 
                                        M08_CBC_HB_LBORRES_5>=0 & M08_CBC_HB_LBORRES_5<7) ~ "severe",
                                      (is.na(M08_CBC_HB_LBORRES_5) & !is.na(M06_HB_POC_LBORRES_5) & 
                                        M06_HB_POC_LBORRES_5>=0 & M06_HB_POC_LBORRES_5<7) ~ "severe",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_5) & 
                                        M08_CBC_HB_LBORRES_5>=11 & M08_CBC_HB_LBORRES_5<=13) ~ "normal",
                                      (is.na(M08_CBC_HB_LBORRES_5) & !is.na(M06_HB_POC_LBORRES_5) & 
                                        M06_HB_POC_LBORRES_5>=11 & M06_HB_POC_LBORRES_5<=13) ~ "normal",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_5) & 
                                        M08_CBC_HB_LBORRES_5>13 & M08_CBC_HB_LBORRES_5<15) ~ "high hb 13-<15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_5) & !is.na(M06_HB_POC_LBORRES_5) & 
                                        M06_HB_POC_LBORRES_5>13 & M06_HB_POC_LBORRES_5<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_5) & M08_CBC_HB_LBORRES_5>=15)  ~ "high hb >=15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_5) & !is.na(M06_HB_POC_LBORRES_5) & 
                                      M06_HB_POC_LBORRES_5>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS5, M08_CBC_HB_LBORRES_5, M06_HB_POC_LBORRES_5)

table(anemia_df$MAT_ANEMIA_MEAS5, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS5, useNA = "always", anemia_df$SITE), margin=2)*100,2)


```

# ANY ANC ANEMIA
```{r}
# ANEMIA MEASURED PREGNANCY ONLY # 
anemia_df <- anemia_df %>%
  mutate(MAT_ANEMIA_MEAS_ANC_ANY = case_when(MAT_ANEMIA_MEAS1 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1, 
                                         MAT_ANEMIA_MEAS2 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS3 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS4 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS5 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS1 %in% c("normal") ~ 0, # IF A WOMAN IS NORMAL IN ANC1 AND MILD IN ANC2, ANSWER WILL BE ANEMIC(1). THIS LINE DOESN'T OVERRIDE
                                         MAT_ANEMIA_MEAS2 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS3 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS4 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS5 %in% c("normal") ~ 0,
                                         TRUE ~ as.numeric(NA)))

table(anemia_df$MAT_ANEMIA_MEAS_ANC_ANY, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS_ANC_ANY, useNA = "always", anemia_df$SITE), margin = 2)*100, 3)
  
```

# INVESTIGATING MISSING ACROSS ALL ANC
```{r}
temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6,
         M08_CBC_HB_LBORRES_1, M06_HB_POC_LBORRES_1,
         M08_CBC_HB_LBORRES_2, M06_HB_POC_LBORRES_2,
         M08_CBC_HB_LBORRES_3, M06_HB_POC_LBORRES_3,
         M08_CBC_HB_LBORRES_4, M06_HB_POC_LBORRES_4,
         M08_CBC_HB_LBORRES_5, M06_HB_POC_LBORRES_5, 
         MAT_ANEMIA_MEAS_ANC_ANY) %>% filter(SITE=='Ghana')

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6,
         MAT_ANEMIA_MEAS1, MAT_ANEMIA_MEAS2,
         MAT_ANEMIA_MEAS3, MAT_ANEMIA_MEAS4,
         MAT_ANEMIA_MEAS5,
         MAT_ANEMIA_MEAS_ANC_ANY) %>% filter(SITE=='Ghana')

```

# ANEMIA IN LABOR AND DELIVERY (IPC)
```{r}
#SETTING UP VISIT 6 - IPC (L&D).
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS6 = case_when((!is.na(M08_CBC_HB_LBORRES_6) & 
                                        M08_CBC_HB_LBORRES_6>=10 & M08_CBC_HB_LBORRES_6<11) ~ "mild",
                                      (is.na(M08_CBC_HB_LBORRES_6) & !is.na(M06_HB_POC_LBORRES_6) & 
                                        M06_HB_POC_LBORRES_6>=10 & M06_HB_POC_LBORRES_6<11) ~ "mild",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_6) & 
                                        M08_CBC_HB_LBORRES_6>=7 & M08_CBC_HB_LBORRES_6<10) ~ "moderate",
                                      (is.na(M08_CBC_HB_LBORRES_6) & !is.na(M06_HB_POC_LBORRES_6) & 
                                        M06_HB_POC_LBORRES_6>=7 & M06_HB_POC_LBORRES_6<10) ~ "moderate",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_6) & 
                                        M08_CBC_HB_LBORRES_6>=0 & M08_CBC_HB_LBORRES_6<7) ~ "severe",
                                      (is.na(M08_CBC_HB_LBORRES_6) & !is.na(M06_HB_POC_LBORRES_6) & 
                                        M06_HB_POC_LBORRES_6>=0 & M06_HB_POC_LBORRES_6<7) ~ "severe",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_6) & 
                                        M08_CBC_HB_LBORRES_6>=11 & M08_CBC_HB_LBORRES_6<=13) ~ "normal",
                                      (is.na(M08_CBC_HB_LBORRES_6) & !is.na(M06_HB_POC_LBORRES_6) & 
                                        M06_HB_POC_LBORRES_6>=11 & M06_HB_POC_LBORRES_6<=13) ~ "normal",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_6) & 
                                        M08_CBC_HB_LBORRES_6>13 & M08_CBC_HB_LBORRES_6<15) ~ "high hb 13-<15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_6) & !is.na(M06_HB_POC_LBORRES_6) & 
                                        M06_HB_POC_LBORRES_6>13 & M06_HB_POC_LBORRES_6<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M08_CBC_HB_LBORRES_6) & M08_CBC_HB_LBORRES_6>=15)  ~ "high hb >=15g/dl",
                                      (is.na(M08_CBC_HB_LBORRES_6) & !is.na(M06_HB_POC_LBORRES_6) & 
                                      M06_HB_POC_LBORRES_6>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS6, M08_CBC_HB_LBORRES_6, M06_HB_POC_LBORRES_6)


table(anemia_df$MAT_ANEMIA_MEAS6, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS6, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)

```

# ANEMIA DURING PNC0 (VISIT 7), PNC1 (VISIT 8), PNC4 (VISIT 9) - ONLY POC Diagnostics (MNH06) is done, not Lab results (MNH08)***
```{r echo=FALSE}

# VISIT 7 - PNC0 (Only POC diagnostics MNH06 available)
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS7 = case_when((is.na(M08_CBC_HB_LBORRES_7) & !is.na(M06_HB_POC_LBORRES_7) & 
                                        M06_HB_POC_LBORRES_7>=10 & M06_HB_POC_LBORRES_7<11) ~ "mild",
                                      
                                      (is.na(M08_CBC_HB_LBORRES_7) & !is.na(M06_HB_POC_LBORRES_7) & 
                                        M06_HB_POC_LBORRES_7>=7 & M06_HB_POC_LBORRES_7<10) ~ "moderate",
                                      
                                      (is.na(M08_CBC_HB_LBORRES_7) & !is.na(M06_HB_POC_LBORRES_7) & 
                                        M06_HB_POC_LBORRES_7>=0 & M06_HB_POC_LBORRES_7<7) ~ "severe",
                                      
                                      (is.na(M08_CBC_HB_LBORRES_7) & !is.na(M06_HB_POC_LBORRES_7) & 
                                        M06_HB_POC_LBORRES_7>=11 & M06_HB_POC_LBORRES_7<=13) ~ "normal",
                                      
                                      (is.na(M08_CBC_HB_LBORRES_7) & !is.na(M06_HB_POC_LBORRES_7) & 
                                        M06_HB_POC_LBORRES_7>13 & M06_HB_POC_LBORRES_7<15) ~ "high hb 13-<15g/dl",
                                      
                                      (is.na(M08_CBC_HB_LBORRES_7) & !is.na(M06_HB_POC_LBORRES_7) & 
                                      M06_HB_POC_LBORRES_7>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS7, M08_CBC_HB_LBORRES_7, M06_HB_POC_LBORRES_7)


table(anemia_df$MAT_ANEMIA_MEAS7, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS7, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)
```

```{r}

# VISIT 8 - PNC 1 (Only POC diagnostics MNH06 available)
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS8 = case_when((!is.na(M06_HB_POC_LBORRES_8) & 
                                        M06_HB_POC_LBORRES_8>=10 & M06_HB_POC_LBORRES_8<11) ~ "mild",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_8) & 
                                        M06_HB_POC_LBORRES_8>=7 & M06_HB_POC_LBORRES_8<10) ~ "moderate",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_8) & 
                                        M06_HB_POC_LBORRES_8>=0 & M06_HB_POC_LBORRES_8<7) ~ "severe",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_8) & 
                                        M06_HB_POC_LBORRES_8>=11 & M06_HB_POC_LBORRES_8<=13) ~ "normal",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_8) & 
                                        M06_HB_POC_LBORRES_8>13 & M06_HB_POC_LBORRES_8<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_8) & 
                                      M06_HB_POC_LBORRES_8>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS8, M06_HB_POC_LBORRES_8)


table(anemia_df$MAT_ANEMIA_MEAS8, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS8, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)
```

# PNC 4
```{r}
  # VISIT 9 - PNC 4 (Only POC Diagnostics MNH06 available)
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS9 = case_when((!is.na(M06_HB_POC_LBORRES_9) & 
                                        M06_HB_POC_LBORRES_9>=10 & M06_HB_POC_LBORRES_9<11) ~ "mild",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_9) & 
                                        M06_HB_POC_LBORRES_9>=7 & M06_HB_POC_LBORRES_9<10) ~ "moderate",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_9) & 
                                        M06_HB_POC_LBORRES_9>=0 & M06_HB_POC_LBORRES_9<7) ~ "severe",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_9) & 
                                        M06_HB_POC_LBORRES_9>=11 & M06_HB_POC_LBORRES_9<=13) ~ "normal",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_9) & 
                                        M06_HB_POC_LBORRES_9>13 & M06_HB_POC_LBORRES_9<15) ~ "high hb 13-<15g/dl",
                                      
                                      (!is.na(M06_HB_POC_LBORRES_9) & 
                                      M06_HB_POC_LBORRES_9>=15) ~ "high hb >=15g/dl",
                                      
                                      TRUE ~ as.character(NA)))

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, MAT_ANEMIA_MEAS9, M06_HB_POC_LBORRES_9)

table(anemia_df$MAT_ANEMIA_MEAS9, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS9, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)

```

# ANY PNC ANEMIA (PNC0, PNC1, PNC4)
```{r}
# ANEMIA MEASURED PNC ONLY # 
anemia_df <- anemia_df %>%
  mutate(MAT_ANEMIA_MEAS_PNC_ANY = case_when(MAT_ANEMIA_MEAS7 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1, 
                                         MAT_ANEMIA_MEAS8 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS9 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS7 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS8 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS9 %in% c("normal") ~ 0,
                                         TRUE ~ as.numeric(NA)))

temp.df <- anemia_df %>% select(MOMID, SITE, MAT_ANEMIA_MEAS_PNC_ANY, MAT_ANEMIA_MEAS7, MAT_ANEMIA_MEAS8, MAT_ANEMIA_MEAS9)

table(anemia_df$MAT_ANEMIA_MEAS_PNC_ANY, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS_PNC_ANY, useNA = "always", anemia_df$SITE), margin = 2)*100, 3)
```

# File for tables:
```{r}
write.csv(anemia_df, '../data_out/anemia_fortables_20231020.csv')
```

