---
title: "Mat_anemia_analysis"
author: "Fouzia Farooq"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(stringr)
# library(ThemePark)
library(purrr)
library(lubridate)
library(readr)
library(tidyr)
library(haven)
library(tableone)
library(kableExtra)

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
anemia_df <- read.csv('data_out/mat_anemia.csv')
```


# Convert "1907-07-07" to NA:
# CATEGORICAL: 
# ---- 77, Not applicable 
# ---- 55, Missing 
# ---- 66, Refused to answer
# ---- 99, Don't know

# CONTINUOUS:
# ---- -7, Not applicable 
# ---- -5, Missing 
# ---- -6, Refused to answer
# ---- -9, Don't know
# DATE: 
# ---- 07-07-1907, Not applicable 
# ---- 05-05-1905, Missing 
# ---- 06-06-1906, Refused to answer
# ---- 09-09-1909, Don't know

# TIME: 
# ---- 77:77, Not applicable 
# ---- 55:55, Missing 
# ---- 66:66, Refused to answer
# ---- 99:99, Don't know
```{r echo=FALSE}
CONVERT_NA <- TRUE
if(CONVERT_NA ==TRUE){
  
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d=="1907-07-07", NA, d)
    })
  
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-7, NA, d)
    })
  
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==77, NA, d)
    })
  
  # -5 IS MISSING FOR CONTINOUS
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-5, NA, d)
    })
  
  # 55 IS MISSING FOR CATEGORICAL
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d==55, NA, d) 
    })
  
  # 55:55 IS MISSING FOR TIME
  anemia_df <- anemia_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d=='55:55', NA, d)
    })
  
}
```

# ANC VISIT 1 - ENROLLMENT
```{r}
anemia_df <- anemia_df %>% filter(DELIVERED_FF==1) # SUBSET TO WOMEN WHO HAD A DELIVERY

anemia_df <- anemia_df %>%
  #SETTING UP VISIT 1 - enrollment.
  # 1st trimester
  mutate(MAT_ANEMIA_MEAS1 = ifelse((!is.na(M08_CBC_HB_LBORRES_1) & between(M08_CBC_HB_LBORRES_1, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_1) & between(M06_HB_POC_LBORRES_1, 10, 10.9)), "mild",
                                          ifelse((!is.na(M08_CBC_HB_LBORRES_1) & between(M08_CBC_HB_LBORRES_1, 7.0, 9.9)), "moderate",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_1) & between(M06_HB_POC_LBORRES_1, 7.0, 9.9)), "moderate",
                                                        ifelse((!is.na(M08_CBC_HB_LBORRES_1) & between(M08_CBC_HB_LBORRES_1, 0.0, 6.9)), "severe",
                                                               ifelse((!is.na(M06_HB_POC_LBORRES_1) & between(M06_HB_POC_LBORRES_1, 0.0, 6.9)), "severe",
                                                                      ifelse((!is.na(M08_CBC_HB_LBORRES_1) & between(M08_CBC_HB_LBORRES_1, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                             ifelse((!is.na(M06_HB_POC_LBORRES_1) & between(M06_HB_POC_LBORRES_1, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                                    ifelse((!is.na(M08_CBC_HB_LBORRES_1) & M08_CBC_HB_LBORRES_1 > 14.9), "high hb >=15g/dl",
                                                                                           ifelse((!is.na(M06_HB_POC_LBORRES_1) & M06_HB_POC_LBORRES_1 > 14.9), "high hb >=15g/dl",
                                                                                                  ifelse((!is.na(M08_CBC_HB_LBORRES_1) & between(M08_CBC_HB_LBORRES_1, 11, 13.0)), "normal",
                                                                                                         ifelse((!is.na(M06_HB_POC_LBORRES_1) & between(M06_HB_POC_LBORRES_1, 11, 13.0)), "normal",
                                                                                                                as.character(NA)))))))))))))) 

sum(anemia_df$M08_CBC_HB_LBORRES_1 %in% c(-5, -7))

table(MAT_ANEMIA_MEAS1 = anemia_df$MAT_ANEMIA_MEAS1, useNA = "always", SITE = anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS1, useNA = "always", anemia_df$SITE), margin=2)*100,2) 

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, M08_CBC_HB_LBORRES_1, M06_HB_POC_LBORRES_1, MAT_ANEMIA_MEAS1) %>% filter(SITE=='Ghana')

temp.df <- temp.df %>% 
  mutate(MISSING_BOTH_ANC1 =  case_when(is.na(M08_CBC_HB_LBORRES_1) & is.na(M06_HB_POC_LBORRES_1) ~ 1, 
                                        TRUE ~ as.numeric(0)))

anemia_df <- anemia_df %>%
  mutate(HIGH_HB_gt15 = case_when(MAT_ANEMIA_MEAS1=="high hb >=15g/dl" ~ 1, TRUE ~0))
```

# VISIT 2
```{r}
# ANEMIA ANC 20 - VISIT 2

anemia_df <- anemia_df %>% 
  #SETTING UP VISIT 2 - ANC20.
  # 2ND TRIMESTER
  mutate(MAT_ANEMIA_MEAS2 = ifelse((!is.na(M08_CBC_HB_LBORRES_2) & between(M08_CBC_HB_LBORRES_2, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_2) & between(M06_HB_POC_LBORRES_2, 10, 10.9)), "mild",
                                          ifelse((!is.na(M08_CBC_HB_LBORRES_2) & between(M08_CBC_HB_LBORRES_2, 7.0, 9.9)), "moderate",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_2) & between(M06_HB_POC_LBORRES_2, 7.0, 9.9)), "moderate",
                                                        ifelse((!is.na(M08_CBC_HB_LBORRES_2) & between(M08_CBC_HB_LBORRES_2, 0.0, 6.9)), "severe",
                                                               ifelse((!is.na(M06_HB_POC_LBORRES_2) & between(M06_HB_POC_LBORRES_2, 0.0, 6.9)), "severe",
                                                                      ifelse((!is.na(M08_CBC_HB_LBORRES_2) & between(M08_CBC_HB_LBORRES_2, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                             ifelse((!is.na(M06_HB_POC_LBORRES_2) & between(M06_HB_POC_LBORRES_2, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                                    ifelse((!is.na(M08_CBC_HB_LBORRES_2) & M08_CBC_HB_LBORRES_2 > 14.9), "high hb >=15g/dl",
                                                                                           ifelse((!is.na(M06_HB_POC_LBORRES_2) & M06_HB_POC_LBORRES_2 > 14.9), "high hb >=15g/dl",
                                                                                                  ifelse((!is.na(M08_CBC_HB_LBORRES_2) & between(M08_CBC_HB_LBORRES_2, 11, 13.0)), "normal",
                                                                                                         ifelse((!is.na(M06_HB_POC_LBORRES_2) & between(M06_HB_POC_LBORRES_2, 11, 13.0)), "normal",
                                                                                                                as.character(NA)))))))))))))) 

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, M08_CBC_HB_LBORRES_2, M06_HB_POC_LBORRES_2, MAT_ANEMIA_MEAS2) %>% filter(SITE=='Ghana')
write.csv(temp.df, 'data_out/temp.df.csv')
table(anemia_df$MAT_ANEMIA_MEAS2, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS2, useNA = "always", anemia_df$SITE), margin=2)*100,2)  

```

# VISIT 3
```{r}
  #SETTING UP VISIT 3 - ANC28.
# 3RD trimester
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS3 = ifelse((!is.na(M08_CBC_HB_LBORRES_3) & between(M08_CBC_HB_LBORRES_3, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_3) & between(M06_HB_POC_LBORRES_3, 10, 10.9)), "mild",
                                          ifelse((!is.na(M08_CBC_HB_LBORRES_3) & between(M08_CBC_HB_LBORRES_3, 7.0, 9.9)), "moderate",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_3) & between(M06_HB_POC_LBORRES_3, 7.0, 9.9)), "moderate",
                                                        ifelse((!is.na(M08_CBC_HB_LBORRES_3) & between(M08_CBC_HB_LBORRES_3, 0.0, 6.9)), "severe",
                                                               ifelse((!is.na(M06_HB_POC_LBORRES_3) & between(M06_HB_POC_LBORRES_3, 0.0, 6.9)), "severe",
                                                                      ifelse((!is.na(M08_CBC_HB_LBORRES_3) & between(M08_CBC_HB_LBORRES_3, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                             ifelse((!is.na(M06_HB_POC_LBORRES_3) & between(M06_HB_POC_LBORRES_3, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                                    ifelse((!is.na(M08_CBC_HB_LBORRES_3) & M08_CBC_HB_LBORRES_3 > 14.9), "high hb >=15g/dl",
                                                                                           ifelse((!is.na(M06_HB_POC_LBORRES_3) & M06_HB_POC_LBORRES_3 > 14.9), "high hb >=15g/dl",
                                                                                                  ifelse((!is.na(M08_CBC_HB_LBORRES_3) & between(M08_CBC_HB_LBORRES_3, 11, 13.0)), "normal",
                                                                                                         ifelse((!is.na(M06_HB_POC_LBORRES_3) & between(M06_HB_POC_LBORRES_3, 11, 13.0)), "normal",
                                                                                                                as.character(NA)))))))))))))) 

table(anemia_df$MAT_ANEMIA_MEAS3, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS3, useNA = "always", anemia_df$SITE), margin=2)*100,2)

```

# VISIT 4
```{r}
  #SETTING UP VISIT 4 - ANC32.
# 3RD TRIMESTER
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS4 = ifelse((!is.na(M08_CBC_HB_LBORRES_4) & between(M08_CBC_HB_LBORRES_4, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_4) & between(M06_HB_POC_LBORRES_4, 10, 10.9)), "mild",
                                          ifelse((!is.na(M08_CBC_HB_LBORRES_4) & between(M08_CBC_HB_LBORRES_4, 7.0, 9.9)), "moderate",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_4) & between(M06_HB_POC_LBORRES_4, 7.0, 9.9)), "moderate",
                                                        ifelse((!is.na(M08_CBC_HB_LBORRES_4) & between(M08_CBC_HB_LBORRES_4, 0.0, 6.9)), "severe",
                                                               ifelse((!is.na(M06_HB_POC_LBORRES_4) & between(M06_HB_POC_LBORRES_4, 0.0, 6.9)), "severe",
                                                                      ifelse((!is.na(M08_CBC_HB_LBORRES_4) & between(M08_CBC_HB_LBORRES_4, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                             ifelse((!is.na(M06_HB_POC_LBORRES_4) & between(M06_HB_POC_LBORRES_4, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                                    ifelse((!is.na(M08_CBC_HB_LBORRES_4) & M08_CBC_HB_LBORRES_4 > 14.9), "high hb >=15g/dl",
                                                                                           ifelse((!is.na(M06_HB_POC_LBORRES_4) & M06_HB_POC_LBORRES_4 > 14.9), "high hb >=15g/dl",
                                                                                                  ifelse((!is.na(M08_CBC_HB_LBORRES_4) & between(M08_CBC_HB_LBORRES_4, 11, 13.0)), "normal",
                                                                                                         ifelse((!is.na(M06_HB_POC_LBORRES_4) & between(M06_HB_POC_LBORRES_4, 11, 13.0)), "normal",
                                                                                                                as.character(NA)))))))))))))) 
  

table(anemia_df$MAT_ANEMIA_MEAS4, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS4, useNA = "always", anemia_df$SITE), margin=2)*100,2)
```

# VISIT 5
```{r}
  #SETTING UP VISIT 5 - ANC36.
# 3RD TRIMESTER
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS5 = ifelse((!is.na(M08_CBC_HB_LBORRES_5) & between(M08_CBC_HB_LBORRES_5, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_5) & between(M06_HB_POC_LBORRES_5, 10, 10.9)), "mild",
                                          ifelse((!is.na(M08_CBC_HB_LBORRES_5) & between(M08_CBC_HB_LBORRES_5, 7.0, 9.9)), "moderate",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_5) & between(M06_HB_POC_LBORRES_5, 7.0, 9.9)), "moderate",
                                                        ifelse((!is.na(M08_CBC_HB_LBORRES_5) & between(M08_CBC_HB_LBORRES_5, 0.0, 6.9)), "severe",
                                                               ifelse((!is.na(M06_HB_POC_LBORRES_5) & between(M06_HB_POC_LBORRES_5, 0.0, 6.9)), "severe",
                                                                      ifelse((!is.na(M08_CBC_HB_LBORRES_5) & between(M08_CBC_HB_LBORRES_5, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                             ifelse((!is.na(M06_HB_POC_LBORRES_5) & between(M06_HB_POC_LBORRES_5, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                                    ifelse((!is.na(M08_CBC_HB_LBORRES_5) & M08_CBC_HB_LBORRES_5 > 14.9), "high hb >=15g/dl",
                                                                                           ifelse((!is.na(M06_HB_POC_LBORRES_5) & M06_HB_POC_LBORRES_5 > 14.9), "high hb >=15g/dl",
                                                                                                  ifelse((!is.na(M08_CBC_HB_LBORRES_5) & between(M08_CBC_HB_LBORRES_5, 11, 13.0)), "normal",
                                                                                                         ifelse((!is.na(M06_HB_POC_LBORRES_5) & between(M06_HB_POC_LBORRES_5, 11, 13.0)), "normal", 

                                                                                                                as.character(NA)))))))))))))) 
  

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6, M08_CBC_HB_LBORRES_5, M06_HB_POC_LBORRES_5, MAT_ANEMIA_MEAS5) %>% filter(SITE=='Ghana')

table(anemia_df$MAT_ANEMIA_MEAS5, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS5, useNA = "always", anemia_df$SITE), margin=2)*100,2)


```

# ANY ANC ANEMIA
```{r}
# ANEMIA MEASURED PREGNANCY ONLY # 
anemia_df <- anemia_df %>%
  mutate(MAT_ANEMIA_MEAS_ANC = case_when(MAT_ANEMIA_MEAS1 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1, 
                                         MAT_ANEMIA_MEAS2 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS3 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS4 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS5 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS1 %in% c("normal") ~ 0, # IF A WOMAN IS NORMAL IN ANC1 AND MILD IN ANC2, ANSWER WILL BE ANEMIC(1). THIS LINE DOESN'T OVERRIDE
                                         MAT_ANEMIA_MEAS2 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS3 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS4 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS5 %in% c("normal") ~ 0,
                                         TRUE ~ as.numeric(NA)))

table(anemia_df$MAT_ANEMIA_MEAS_ANC, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS_ANC, useNA = "always", anemia_df$SITE), margin = 2)*100, 3)
  
```

# INVESTIGATING MISSING ACROSS ALL ANC
```{r}
temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6,
         M08_CBC_HB_LBORRES_1, M06_HB_POC_LBORRES_1,
         M08_CBC_HB_LBORRES_2, M06_HB_POC_LBORRES_2,
         M08_CBC_HB_LBORRES_3, M06_HB_POC_LBORRES_3,
         M08_CBC_HB_LBORRES_4, M06_HB_POC_LBORRES_4,
         M08_CBC_HB_LBORRES_5, M06_HB_POC_LBORRES_5, 
         MAT_ANEMIA_MEAS_ANC) %>% filter(SITE=='Ghana')

temp.df <- anemia_df %>%
  select(SITE, MOMID, DELIVERED_FF, M09_DELIV_DSSTDAT_INF1_6,
         MAT_ANEMIA_MEAS1, MAT_ANEMIA_MEAS2,
         MAT_ANEMIA_MEAS3, MAT_ANEMIA_MEAS4,
         MAT_ANEMIA_MEAS5,
         MAT_ANEMIA_MEAS_ANC) %>% filter(SITE=='Ghana')

```

# ANEMIA IN LABOR AND DELIVERY (IPC)
```{r}
#SETTING UP VISIT 6 - IPC (L&D).
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS6 = ifelse((!is.na(M08_CBC_HB_LBORRES_6) & between(M08_CBC_HB_LBORRES_6, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_6) & between(M06_HB_POC_LBORRES_6, 10, 10.9)), "mild",
                                          ifelse((!is.na(M08_CBC_HB_LBORRES_6) & between(M08_CBC_HB_LBORRES_6, 7.0, 9.9)), "moderate",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_6) & between(M06_HB_POC_LBORRES_6, 7.0, 9.9)), "moderate",
                                                        ifelse((!is.na(M08_CBC_HB_LBORRES_6) & between(M08_CBC_HB_LBORRES_6, 0.0, 6.9)), "severe",
                                                               ifelse((!is.na(M06_HB_POC_LBORRES_6) & between(M06_HB_POC_LBORRES_6, 0.0, 6.9)), "severe",
                                                                      ifelse((!is.na(M08_CBC_HB_LBORRES_6) & between(M08_CBC_HB_LBORRES_6, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                             ifelse((!is.na(M06_HB_POC_LBORRES_6) & between(M06_HB_POC_LBORRES_6, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                                                    ifelse((!is.na(M08_CBC_HB_LBORRES_6) & M08_CBC_HB_LBORRES_6 > 14.9), "high hb >=15g/dl",
                                                                                           ifelse((!is.na(M06_HB_POC_LBORRES_6) & M06_HB_POC_LBORRES_6 > 14.9), "high hb >=15g/dl",
                                                                                                  ifelse((!is.na(M08_CBC_HB_LBORRES_6) & between(M08_CBC_HB_LBORRES_6, 11, 13.0)), "normal",
                                                                                                         ifelse((!is.na(M06_HB_POC_LBORRES_6) & between(M06_HB_POC_LBORRES_6, 11, 13.0)), "normal",# "normal")))))))))))))


                                                                                                                as.character(NA)))))))))))))) 

table(anemia_df$MAT_ANEMIA_MEAS6, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS6, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)

```

# ANEMIA DURING PNC0 (VISIT 7), PNC1 (VISIT 8), PNC4 (VISIT 9) - ONLY POC Diagnostics (MNH06) is done, not Lab results (MNH08)***
```{r echo=FALSE}
anemia_df <- anemia_df %>%
  # VISIT 7 - PNC 0
  mutate(MAT_ANEMIA_MEAS7 = ifelse((!is.na(M06_HB_POC_LBORRES_7) & between(M06_HB_POC_LBORRES_7, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_7) & between(M06_HB_POC_LBORRES_7, 7.0, 9.9)), "moderate",
                                          ifelse((!is.na(M06_HB_POC_LBORRES_7) & between(M06_HB_POC_LBORRES_7, 0.0, 6.9)), "severe",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_7) & between(M06_HB_POC_LBORRES_7, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                        ifelse((!is.na(M06_HB_POC_LBORRES_7) & M06_HB_POC_LBORRES_7 > 14.9), "high hb >=15g/dl",
                                                        ifelse((!is.na(M06_HB_POC_LBORRES_7) & between(M06_HB_POC_LBORRES_7, 11, 13.0)), "normal",
                                                               as.character(NA))))))))

temp.df <- anemia_df %>% select(MOMID, SITE, M06_HB_POC_LBORRES_7, MAT_ANEMIA_MEAS7) %>% filter(SITE == "Pakistan")
table(anemia_df$MAT_ANEMIA_MEAS7, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS7, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)
```

```{r}
  # VISIT 8 - PNC 1
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS8 = ifelse((!is.na(M06_HB_POC_LBORRES_8) & between(M06_HB_POC_LBORRES_8, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_8) & between(M06_HB_POC_LBORRES_8, 7.0, 9.9)), "moderate",
                                          ifelse((!is.na(M06_HB_POC_LBORRES_8) & between(M06_HB_POC_LBORRES_8, 0.0, 6.9)), "severe",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_8) & between(M06_HB_POC_LBORRES_8, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                        ifelse((!is.na(M06_HB_POC_LBORRES_8) & M06_HB_POC_LBORRES_8 > 14.9), "high hb >=15g/dl",
                                                        ifelse((!is.na(M06_HB_POC_LBORRES_8) & between(M06_HB_POC_LBORRES_8, 11, 13.0)), "normal",
                                                               as.character(NA))))))))

table(anemia_df$MAT_ANEMIA_MEAS8, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS8, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)
```

# PNC 4
```{r}
  # VISIT 9 - PNC 4
anemia_df <- anemia_df %>% 
  mutate(MAT_ANEMIA_MEAS9 = ifelse((!is.na(M06_HB_POC_LBORRES_9) & between(M06_HB_POC_LBORRES_9, 10, 10.9)), "mild",
                                   ifelse((!is.na(M06_HB_POC_LBORRES_9) & between(M06_HB_POC_LBORRES_9, 7.0, 9.9)), "moderate",
                                          ifelse((!is.na(M06_HB_POC_LBORRES_9) & between(M06_HB_POC_LBORRES_9, 0.0, 6.9)), "severe",
                                                 ifelse((!is.na(M06_HB_POC_LBORRES_9) & between(M06_HB_POC_LBORRES_9, 13.1, 14.9)), "high hb 13-<15g/dl",
                                                        ifelse((!is.na(M06_HB_POC_LBORRES_9) & M06_HB_POC_LBORRES_9 > 14.9), "high hb >=15g/dl",
                                                        ifelse((!is.na(M06_HB_POC_LBORRES_9) & between(M06_HB_POC_LBORRES_9, 11, 13.0)), "normal",
                                                               as.character(NA))))))))

table(anemia_df$MAT_ANEMIA_MEAS9, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS9, useNA = "always", anemia_df$SITE), margin = 2)*100, 2)

```

# ANY PNC ANEMIA (PNC0, PNC1, PNC4)
```{r}
# ANEMIA MEASURED PNC ONLY # 
anemia_df <- anemia_df %>%
  mutate(MAT_ANEMIA_MEAS_PNC = case_when(MAT_ANEMIA_MEAS7 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1, 
                                         MAT_ANEMIA_MEAS8 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS9 %in% c("severe", "mild", "moderate", "high hb 13-<15g/dl", "high hb >=15g/dl") ~ 1,
                                         MAT_ANEMIA_MEAS7 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS8 %in% c("normal") ~ 0,
                                         MAT_ANEMIA_MEAS9 %in% c("normal") ~ 0,
                                         TRUE ~ as.numeric(NA)))

table(anemia_df$MAT_ANEMIA_MEAS_PNC, useNA = "always", anemia_df$SITE)
round(prop.table(table(anemia_df$MAT_ANEMIA_MEAS_PNC, useNA = "always", anemia_df$SITE), margin = 2)*100, 3)
```