---
title:  "<span style='font-size: 18px'> <span style='text-align: center'> PRISMA Sphb and CBC Hb analysis - Bland Altman Plots (Issued: `r Sys.Date()`)"
author: "Author: Fouzia Farooq"
output:
  pdf_document:
    df_print: paged
    toc: yes
    toc_depth: 4
 

---

&nbsp;
&nbsp;
&nbsp;
&nbsp;


##### **Includes data from synapse last updated:** {.unlisted .unnumbered}
#####  Kenya: 2023-10-13 {.unlisted .unnumbered}
#####  Pakistan: 2023-10-13 {.unlisted .unnumbered}
#####  Zambia: 2023-10-13 {.unlisted .unnumbered}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
# library(gfoRmula)
# library(R.utils)
library(dplyr)
library(irr)
library(knitr)
library(kableExtra)
```


```{r include=FALSE}
sphb_df <- read.csv('../data_out/mat_Sphb.csv', header = TRUE)
window_subset_df <- read.csv('../data_out/window_subset_df.csv', header = TRUE)
sphb_df <- sphb_df %>% filter(SITE=="Pakistan" | SITE=="Zambia" | SITE=="Kenya")
```


```{r include=FALSE}

# Convert "1907-07-07" to NA:
# CATEGORICAL: 
# ---- 77, Not applicable 
# ---- 55, Missing 
# ---- 66, Refused to answer
# ---- 99, Don't know

# CONTINUOUS:
# ---- -7, Not applicable 
# ---- -5, Missing 
# ---- -6, Refused to answer
# ---- -9, Don't know
# DATE: 
# ---- 07-07-1907, Not applicable 
# ---- 05-05-1905, Missing 
# ---- 06-06-1906, Refused to answer
# ---- 09-09-1909, Don't know

# TIME: 
# ---- 77:77, Not applicable 
# ---- 55:55, Missing 
# ---- 66:66, Refused to answer
# ---- 99:99, Don't know

CONVERT_NA <- TRUE
if(CONVERT_NA ==TRUE){
  
  sphb_df <- sphb_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d=="1907-07-07", NA, d)
    })
  
  sphb_df <- sphb_df %>% 
    mutate_all(function(d) {
      if_else(d==-7, NA, d)
    })
  
  sphb_df <- sphb_df %>% 
    mutate_all(function(d) {
      if_else(d==77, NA, d)
    })
  
  # -5 IS MISSING FOR CONTINOUS
  sphb_df <- sphb_df %>% 
    mutate_all(function(d) {
      if_else(d==-5, NA, d)
    })
  
  # 55 IS MISSING FOR CATEGORICAL
  sphb_df <- sphb_df %>% 
    mutate_all(function(d) {
      if_else(d==55, NA, d) 
    })
  
  # 55:55 IS MISSING FOR TIME
  sphb_df <- sphb_df %>% 
    mutate_all(function(d) {
      if_else(d=='55:55', NA, d)
    })
}
```


```{r include=FALSE}
# https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4913118/

 # Absolute agreement concerns if different raters assign the same score to the same subject. Conversely, consistency definition concerns if raters’ scores to the same group of subjects are correlated in an additive manner.18 Consider an interrater reliability study of 2 raters as an example. In this case, consistency definition concerns the degree to which one rater’s score (y) can be equated to another rater’s score (x) plus a systematic error (c) (ie, y = x + c), whereas absolute agreement concerns about the extent to which y equals x. -->
# INSPECTING THE DATA -->
  
temp.df <- sphb_df %>% select(MOMID, SITE, M08_CBC_HB_LBORRES_1, M06_SPHB_LBORRES_1)
```


```{r include=FALSE}
# REMOVE THIS CHUNCK.
# 1. CALC. DIFFERENCE IN THE TWO MEASUREMENTS 

# sphb_df <- sphb_df %>% mutate(diff.enroll = M08_CBC_HB_LBORRES_1 - M06_SPHB_LBORRES_1,
#                               diff.anc20 = M08_CBC_HB_LBORRES_2 - M06_SPHB_LBORRES_2,
#                               diff.anc28 = M08_CBC_HB_LBORRES_3 - M06_SPHB_LBORRES_3,
#                               diff.anc32 = M08_CBC_HB_LBORRES_4 - M06_SPHB_LBORRES_4,
#                               diff.anc36 = M08_CBC_HB_LBORRES_5 - M06_SPHB_LBORRES_5,
#                               diff.pnc6 = M08_CBC_HB_LBORRES_10 - M06_SPHB_LBORRES_10)
# 
# temp.df <- sphb_df %>% select(MOMID, SITE, M08_CBC_HB_LBORRES_1, M06_SPHB_LBORRES_1, diff.anc20)
# temp.df <- sphb_df %>% select(MOMID, SITE, M08_CBC_HB_LBORRES_10, M06_SPHB_LBORRES_10, diff.pnc6)
```

```{r include=FALSE}
# 1. CALC. DIFFERENCE IN THE TWO MEASUREMENTS 

sphb_df <- sphb_df %>% mutate(diff.enroll = M06_SPHB_LBORRES_1 - M08_CBC_HB_LBORRES_1,
                              diff.anc20 =  M06_SPHB_LBORRES_2 - M08_CBC_HB_LBORRES_2,
                              diff.anc28 =  M06_SPHB_LBORRES_3- M08_CBC_HB_LBORRES_3,
                              diff.anc32 =  M06_SPHB_LBORRES_4 - M08_CBC_HB_LBORRES_4,
                              diff.anc36 = M06_SPHB_LBORRES_5 - M08_CBC_HB_LBORRES_5,
                              diff.pnc6 =  M06_SPHB_LBORRES_10 - M08_CBC_HB_LBORRES_10)

temp.df <- sphb_df %>% select(MOMID, SITE, M08_CBC_HB_LBORRES_1, M06_SPHB_LBORRES_1, diff.anc20)
temp.df <- sphb_df %>% select(MOMID, SITE, M08_CBC_HB_LBORRES_10, M06_SPHB_LBORRES_10, diff.pnc6)
```


```{r include=FALSE}
# 2. CALC. AVERAGE B/W THE TWO MEASUREMETNS

sphb_df <- sphb_df %>% mutate(avg.enroll = (M08_CBC_HB_LBORRES_1 + M06_SPHB_LBORRES_1)*0.5,
                              avg.anc20 = (M08_CBC_HB_LBORRES_2 + M06_SPHB_LBORRES_2)*0.5,
                              avg.anc28 = (M08_CBC_HB_LBORRES_3 + M06_SPHB_LBORRES_3)*0.5,
                              avg.anc32 = (M08_CBC_HB_LBORRES_4 + M06_SPHB_LBORRES_4)*0.5,
                              avg.anc36 = (M08_CBC_HB_LBORRES_5 + M06_SPHB_LBORRES_5)*0.5,
                              avg.pnc6 =(M08_CBC_HB_LBORRES_10 + M06_SPHB_LBORRES_10)*0.5)
```


```{r include=FALSE}
# 3. CALC. THE AVERAGE DIFFERENT AND 95%CI

# AVERAGE DIFF
# mean_diff.enroll <- mean(sphb_df$diff.enroll, na.rm=TRUE)
# mean_diff.anc20 <- mean(sphb_df$diff.anc20, na.rm=TRUE)
# mean_diff.anc28 <- mean(sphb_df$diff.anc28, na.rm=TRUE)
# mean_diff.anc32 <- mean(sphb_df$diff.anc32, na.rm=TRUE)
# mean_diff.anc36 <- mean(sphb_df$diff.anc36, na.rm=TRUE)
# mean_diff.pnc6 <- mean(sphb_df$diff.pnc6, na.rm=TRUE)
# 
# # LOWER 95%CI
# lower.ci.enroll <- mean_diff.enroll - 1.96*sd(sphb_df$diff.enroll, na.rm=TRUE)
# lower.ci.anc20 <- mean_diff.anc20 - 1.96*sd(sphb_df$diff.anc20, na.rm=TRUE)
# lower.ci.anc28 <- mean_diff.anc28 - 1.96*sd(sphb_df$diff.anc28, na.rm=TRUE)
# lower.ci.anc32 <- mean_diff.anc32 - 1.96*sd(sphb_df$diff.anc32, na.rm=TRUE)
# lower.ci.anc36 <- mean_diff.anc36 - 1.96*sd(sphb_df$diff.anc36, na.rm=TRUE)
# lower.ci.pnc6 <- mean_diff.pnc6 - 1.96*sd(sphb_df$diff.pnc6, na.rm=TRUE)
# 
# 
# # UPPER 95%CI
# upper.ci.enroll <- mean_diff.enroll + 1.96*sd(sphb_df$diff.enroll, na.rm=TRUE)
# upper.ci.anc20 <- mean_diff.anc20 + 1.96*sd(sphb_df$diff.anc20, na.rm=TRUE)
# upper.ci.anc28 <- mean_diff.anc28 + 1.96*sd(sphb_df$diff.anc28, na.rm=TRUE)
# upper.ci.anc32 <- mean_diff.anc32 + 1.96*sd(sphb_df$diff.anc32, na.rm=TRUE)
# upper.ci.anc36 <- mean_diff.anc36 + 1.96*sd(sphb_df$diff.anc36, na.rm=TRUE)
# upper.ci.pnc6 <- mean_diff.pnc6 + 1.96*sd(sphb_df$diff.pnc6, na.rm=TRUE)
```

```{r}
# 3. CALC. THE AVERAGE DIFFERENT AND 95%CI

# AVERAGE DIFF
site_mean_diff_df <- sphb_df %>%
  group_by(SITE) %>% 
  summarize(
    mean_diff.enroll = mean( diff.enroll, na.rm=TRUE),
    mean_diff.anc20 = mean( diff.anc20, na.rm=TRUE),
    mean_diff.anc28 = mean( diff.anc28, na.rm=TRUE),
    mean_diff.anc32 = mean( diff.anc32, na.rm=TRUE),
    mean_diff.anc36 = mean( diff.anc36, na.rm=TRUE),
    mean_diff.pnc6 = mean( diff.pnc6, na.rm=TRUE),
    
    # LOWER 95%CI
    lower.ci.enroll = mean_diff.enroll - 1.96*sd( diff.enroll, na.rm=TRUE),
    lower.ci.anc20 = mean_diff.anc20 - 1.96*sd( diff.anc20, na.rm=TRUE),
    lower.ci.anc28 = mean_diff.anc28 - 1.96*sd( diff.anc28, na.rm=TRUE),
    lower.ci.anc32 = mean_diff.anc32 - 1.96*sd( diff.anc32, na.rm=TRUE),
    lower.ci.anc36 = mean_diff.anc36 - 1.96*sd( diff.anc36, na.rm=TRUE),
    lower.ci.pnc6 = mean_diff.pnc6 - 1.96*sd( diff.pnc6, na.rm=TRUE),
    
    
    # UPPER 95%CI
    upper.ci.enroll = mean_diff.enroll + 1.96*sd( diff.enroll, na.rm=TRUE),
    upper.ci.anc20 = mean_diff.anc20 + 1.96*sd( diff.anc20, na.rm=TRUE),
    upper.ci.anc28 = mean_diff.anc28 + 1.96*sd( diff.anc28, na.rm=TRUE),
    upper.ci.anc32 = mean_diff.anc32 + 1.96*sd( diff.anc32, na.rm=TRUE),
    upper.ci.anc36 = mean_diff.anc36 + 1.96*sd( diff.anc36, na.rm=TRUE),
    upper.ci.pnc6 = mean_diff.pnc6 + 1.96*sd( diff.pnc6, na.rm=TRUE))
```

```{r eval=FALSE, message=FALSE, include=FALSE}
write.csv(sphb_df, '../data_out/Mat_sphb_20231027.csv')
```

```{r}
sphb_df <- left_join(sphb_df, site_mean_diff_df, by = "SITE")
sphb_df <- sphb_df %>% 
  mutate(within.ci.enroll = between(diff.enroll, lower.ci.enroll, upper.ci.enroll), 
         within.ci.anc20 = between(diff.anc20, lower.ci.anc20, upper.ci.anc20),
         within.ci.anc28 = between(diff.anc28, lower.ci.anc28, upper.ci.anc28),
         within.ci.anc32 = between(diff.anc32, lower.ci.anc32, upper.ci.anc32),
         within.ci.anc36 = between(diff.anc36, lower.ci.anc36, upper.ci.anc36))
```

### Figure 1a. Agreement between Enrollment Sphb and Hgb  
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.dim=c(6,6)}
# Create the legend breaks and labels
legend_breaks <- c("Values within 95% limits of agreement", "Values above or 95% limits of agreement")
legend_labels <- c("Within 95% limits of agreement", "Above or below 95% limits of agreement")

sphb_df %>% 
  filter(!is.na(within.ci.enroll)) %>% 
  ggplot(aes(x = avg.enroll, y = diff.enroll, color = within.ci.enroll)) +
  geom_point(size=1.5, alpha = 0.3) +
  scale_color_manual(values = c("red", "blue3")) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = mean_diff.enroll)) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = lower.ci.enroll), color = "red", linetype="dashed") +
  geom_hline(data = site_mean_diff_df, aes(yintercept = upper.ci.enroll), color = "red", linetype="dashed") +
  # ggtitle("Bland-Altman Plot") +
  ylab("Difference Between Measurements at Enrollment visit") +
  xlab("Average Hemoglobin Measurement (g/dl)") + 
  # ggtitle('Agreement between Enrollment Sphb and Hgb')+
  theme_bw() +
  facet_grid(vars(SITE), scales = "free") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  theme(legend.position = "right") + 
  ylim(-10, 10) 


ggsave('../plots/BAplot_enroll.pdf', plot = last_plot(), height = 8, width = 7)
```

\newpage
#### Figure 1b. Relationship between Enrollment Sphb and Hgb 
```{r}
# SCATTER PLOT:
# Create a scatter plot using ggplot2
ggplot(sphb_df, aes(x=M08_CBC_HB_LBORRES_1, y=M06_SPHB_LBORRES_1)) +
  geom_point(alpha=0.4) +
  facet_grid(~ SITE) + 
  labs(title = "Enrollment", x = "CBC Hb (mg/dl)", y = "Sphb (mg/dl)") + 
  ylim(0, 20) + 
  xlim(0,20) +
  geom_abline(slope=1, intercept=0, linetype = "dashed", color = "red") + 
    geom_smooth(method = "lm", se = TRUE, color = "blue")  # Add a linear regression line
```

```{r eval=FALSE, message=FALSE, include=FALSE}
# INTRACLASS CORRELATION - ENROLLMENT

icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_1, M08_CBC_HB_LBORRES_1) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  icc_results_site <- data.frame(SITE = site, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  icc_results <- rbind(icc_results, icc_results_site)
}

icc_results <- icc_results %>% mutate('95%CI' = paste0("(", format(round(Lower,3),nsmall=2, digits=3), ", ", format(round(Upper,3),nsmall=2, digits=3), ")"))
icc_results <- icc_results %>% rename(Site = SITE) %>% select(-Upper, -Lower)
icc_results$ICC <- format(round(icc_results$ICC, 3), nsmall=2, digits=3)
```

```{r eval=FALSE, message=FALSE, include=FALSE}
icc_table <- kable(icc_results, format = "markdown", col.names = c("SITE", "ICC", "Lower", "Upper"), align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

# Add light blue background color to the header row
icc_table <- icc_table %>%
  row_spec(0, background = "lightblue")

icc_table
```

```{r}
# PEARSON CORRELATION: ENROLLMENT

corr_enroll <- sphb_df %>%
  group_by(SITE) %>%
  summarize(correlation = cor(M06_SPHB_LBORRES_1, M08_CBC_HB_LBORRES_1, use = "pairwise.complete.obs")) %>%
  ungroup()

corr_enroll


# PEARSON CORRELATION:ANC-20
corr_anc20 <- sphb_df %>%
  group_by(SITE) %>%
  summarize(correlation = cor(M06_SPHB_LBORRES_2, M08_CBC_HB_LBORRES_2, use = "pairwise.complete.obs")) %>%
  ungroup()

corr_anc20

# PEARSON CORRELATION:ANC-28
corr_anc28 <- sphb_df %>%
  group_by(SITE) %>%
  summarize(correlation = cor(M06_SPHB_LBORRES_3, M08_CBC_HB_LBORRES_3, use = "pairwise.complete.obs")) %>%
  ungroup()

corr_anc28

# PEARSON CORRELATION:ANC-32
corr_anc32 <- sphb_df %>%
  group_by(SITE) %>%
  summarize(correlation = cor(M06_SPHB_LBORRES_4, M08_CBC_HB_LBORRES_4, use = "pairwise.complete.obs")) %>%
  ungroup()

corr_anc32

# PEARSON CORRELATION:ANC-36
corr_anc36 <- sphb_df %>%
  group_by(SITE) %>%
  summarize(correlation = cor(M06_SPHB_LBORRES_5, M08_CBC_HB_LBORRES_5, use = "pairwise.complete.obs")) %>%
  ungroup()

corr_anc36
```



### Figure 2a. Agreement between ANC-20 Sphb and Hgb  
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.dim=c(6,6)}

sphb_df %>% 
  filter(!is.na(within.ci.anc20)) %>% 
  ggplot(aes(x = avg.enroll, y = diff.anc20, color = within.ci.anc20)) +
  geom_point(size=1.5, alpha = 0.3) +
  scale_color_manual(values = c("red", "blue3")) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = mean_diff.anc20)) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = lower.ci.anc20), color = "red", linetype="dashed") +
  geom_hline(data = site_mean_diff_df, aes(yintercept = upper.ci.anc20), color = "red", linetype="dashed") +
  # ggtitle("Bland-Altman Plot") +
  ylab("Difference Between Measurements at ANC-20 visit") +
  xlab("Average Hemoglobin Measurement (g/dl)") + 
  # ggtitle('Agreement between Enrollment Sphb and Hgb')+
  theme_bw() +
  facet_grid(vars(SITE), scales = "free") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  theme(legend.position = "right") + 
  ylim(-8, 8)

ggsave('../plots/BAplot_anc20.jpeg', plot = last_plot(), height = 8, width = 7)
```

#### Figure 2b. Relationship between ANC-20 Sphb and Hgb 
```{r}
# SCATTER PLOT:
# Create a scatter plot using ggplot2
ggplot(sphb_df, aes(x=M08_CBC_HB_LBORRES_2, y=M06_SPHB_LBORRES_2)) +
  geom_point(alpha=0.4) +
  facet_grid(~ SITE) + 
  labs(title = "ANC-20", x = "CBC Hb (mg/dl)", y = "Sphb (mg/dl)") + 
  ylim(0, 20) + 
  xlim(0,20) +
  geom_abline(slope=1, intercept=0, linetype = "dashed", color = "red") + 
    geom_smooth(method = "lm", se = TRUE, color = "blue")  # Add a linear regression line
```

```{r eval=FALSE, message=FALSE, include=FALSE}
# INTRACLASS CORRELATION - VISIT 2

icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_2, M08_CBC_HB_LBORRES_2) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  icc_results_site <- data.frame(SITE = site, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  icc_results <- rbind(icc_results, icc_results_site)
}
```

```{r eval=FALSE, message=FALSE, include=FALSE}
icc_table <- kable(icc_results, format = "markdown", col.names = c("SITE", "ICC", "Lower", "Upper"), align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

# Add light blue background color to the header row
icc_table <- icc_table %>%
  row_spec(0, background = "lightblue")

icc_table
```

### Figure 3a. Agreement between ANC-28 Sphb and Hgb  
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.dim=c(6,6)}

sphb_df %>% 
  filter(!is.na(within.ci.anc28)) %>% 
  ggplot(aes(x = avg.anc28, y = diff.anc28, color = within.ci.anc28)) +
  geom_point(size=1.5, alpha = 0.3) +
  scale_color_manual(values = c("red", "blue3")) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = mean_diff.anc28)) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = lower.ci.anc28), color = "red", linetype="dashed") +
  geom_hline(data = site_mean_diff_df, aes(yintercept = upper.ci.anc28), color = "red", linetype="dashed") +
  # ggtitle("Bland-Altman Plot") +
  ylab("Difference Between Measurements at ANC-28 visit") +
  xlab("Average Hemoglobin Measurement (g/dl)") + 
  # ggtitle('Agreement between anc28ment Sphb and Hgb')+
  theme_bw() +
  facet_grid(vars(SITE), scales = "free") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  theme(legend.position = "right") + 
  ylim(-5, 5)

ggsave('../plots/BAplot_anc28.jpeg', plot = last_plot(), height = 8, width = 7)
```

#### Figure 3b. Relationship between ANC-28 Sphb and Hgb 
```{r}
# SCATTER PLOT:
# Create a scatter plot using ggplot2
ggplot(sphb_df, aes(x=M08_CBC_HB_LBORRES_3, y=M06_SPHB_LBORRES_3)) +
  geom_point(alpha=0.4) +
  facet_grid(~ SITE) + 
  labs(title = "ANC-28", x = "CBC Hb (mg/dl)", y = "Sphb (mg/dl)") + 
  ylim(0, 20) + 
  xlim(0,20) +
  geom_abline(slope=1, intercept=0, linetype = "dashed", color = "red") + 
    geom_smooth(method = "lm", se = TRUE, color = "blue")  # Add a linear regression line
```

```{r eval=FALSE, message=FALSE, include=FALSE}
# INTRACLASS CORRELATION - VISIT 3
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_3, M08_CBC_HB_LBORRES_3) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  icc_results_site <- data.frame(SITE = site, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  icc_results <- rbind(icc_results, icc_results_site)
}
```

```{r eval=FALSE, message=FALSE, include=FALSE}
icc_table <- kable(icc_results, format = "markdown", col.names = c("SITE", "ICC", "Lower", "Upper"), align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

# Add light blue background color to the header row
icc_table <- icc_table %>%
  row_spec(0, background = "lightblue")

icc_table
```

### Figure 4a. Agreement between ANC-32 Sphb and Hgb (Pakistan site)
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.dim=c(6,6)}

sphb_df %>% 
  filter(!is.na(within.ci.anc32)) %>% 
  ggplot(aes(x = avg.anc32, y = diff.anc32, color = within.ci.anc32)) +
  geom_point(size=1.5, alpha = 0.3) +
  scale_color_manual(values = c("red", "blue3")) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = mean_diff.anc32)) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = lower.ci.anc32), color = "red", linetype="dashed") +
  geom_hline(data = site_mean_diff_df, aes(yintercept = upper.ci.anc32), color = "red", linetype="dashed") +
  # ggtitle("Bland-Altman Plot") +
  ylab("Difference Between Measurements at ANC-32 visit") +
  xlab("Average Hemoglobin Measurement (g/dl)") + 
  # ggtitle('Agreement between anc32ment Sphb and Hgb')+
  theme_bw() +
  facet_grid(vars(SITE), scales = "free") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  theme(legend.position = "right") + 
  ylim(-6, 6)


ggsave('../plots/BAplot_anc32.jpeg', plot = last_plot(), height = 8, width = 7)
```

#### Figure 4b. Relationship between ANC-32 Sphb and Hgb 
```{r}
# SCATTER PLOT:
# Create a scatter plot using ggplot2
ggplot(sphb_df, aes(x=M08_CBC_HB_LBORRES_4, y=M06_SPHB_LBORRES_5)) +
  geom_point(alpha=0.4) +
  facet_grid(~ SITE) + 
  labs(title = "ANC-32", x = "CBC Hb (mg/dl)", y = "Sphb (mg/dl)") + 
  ylim(0, 20) + 
  xlim(0,20) +
  geom_abline(slope=1, intercept=0, linetype = "dashed", color = "red") + 
    geom_smooth(method = "lm", se = TRUE, color = "blue")  # Add a linear regression line
```

```{r eval=FALSE, message=FALSE, include=FALSE}
# INTRACLASS CORRELATION - VISIT 4
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_4, M08_CBC_HB_LBORRES_4) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  icc_results_site <- data.frame(SITE = site, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  icc_results <- rbind(icc_results, icc_results_site)
}
```

```{r eval=FALSE, message=FALSE, include=FALSE}
icc_table <- kable(icc_results, format = "markdown", col.names = c("SITE", "ICC", "Lower", "Upper"), align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

# Add light blue background color to the header row
icc_table <- icc_table %>%
  row_spec(0, background = "lightblue")

icc_table
```

### Figure 5. Agreement between ANC-36 Sphb and Hgb 
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.dim=c(6,6)}

sphb_df %>% 
  filter(!is.na(within.ci.anc36)) %>% 
  ggplot(aes(x = avg.anc36, y = diff.anc36, color = within.ci.anc36)) +
  geom_point(size=1.5, alpha = 0.3) +
  scale_color_manual(values = c("red", "blue3")) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = mean_diff.anc36)) +
  geom_hline(data = site_mean_diff_df, aes(yintercept = lower.ci.anc36), color = "red", linetype="dashed") +
  geom_hline(data = site_mean_diff_df, aes(yintercept = upper.ci.anc36), color = "red", linetype="dashed") +
  # ggtitle("Bland-Altman Plot") +
  ylab("Difference Between Measurements at ANC-36 visit") +
  xlab("Average Hemoglobin Measurement (g/dl)") + 
  # ggtitle('Agreement between anc36ment Sphb and Hgb')+
  theme_bw() +
  facet_grid(vars(SITE), scales = "free") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  theme(legend.position = "right") + 
  ylim(-5, 5) 


ggsave('../plots/BAplot_anc36.jpeg', plot = last_plot(), height = 8, width = 7)
```

#### Figure 5b. Relationship between ANC-36 Sphb and Hgb 
```{r}
# SCATTER PLOT:
# Create a scatter plot using ggplot2
ggplot(sphb_df, aes(x=M08_CBC_HB_LBORRES_5, y=M06_SPHB_LBORRES_5)) +
  geom_point(alpha=0.4) +
  facet_grid(~ SITE) + 
  labs(title = "ANC-36", x = "CBC Hb (mg/dl)", y = "Sphb (mg/dl)") + 
  ylim(0, 20) + 
  xlim(0,20) +
  geom_abline(slope=1, intercept=0, linetype = "dashed", color = "red") + 
    geom_smooth(method = "lm", se = TRUE, color = "blue")  # Add a linear regression line
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# INTRACLASS CORRELATION - VISIT 5

icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_5, M08_CBC_HB_LBORRES_5) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  icc_results_site <- data.frame(SITE = site, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  icc_results <- rbind(icc_results, icc_results_site)
}
```

```{r eval=FALSE, message=FALSE, include=FALSE}
icc_table <- kable(icc_results, format = "markdown", col.names = c("SITE", "ICC", "Lower", "Upper"), align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

# Add light blue background color to the header row
icc_table <- icc_table %>%
  row_spec(0, background = "lightblue")

icc_table
```


```{r eval=FALSE, message=FALSE, include=FALSE, fig.dim=c(6,6)}
# CRAETE BLAND-ALTMAN PLOT - PNC6 VISIT 10
color_above <- upper.ci.pnc6
color_below <- lower.ci.pnc6

sphb_df$color <- ifelse(sphb_df$diff.pnc6 > color_above, "red",
                        ifelse(sphb_df$diff.pnc6 < color_below, "red", "blue3"))

ggplot(sphb_df, aes(x = avg.pnc6, y = diff.pnc6, color = color)) +
  geom_point(size=2, alpha = 0.3) +
  scale_color_manual(values = c("blue3", "red", "red")) + 
  geom_hline(yintercept = mean_diff.pnc6) +
  geom_hline(yintercept = lower.ci.pnc6, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper.ci.pnc6, color = "red", linetype="dashed") +
  ggtitle("Bland-Altman Plot") +
  ylab("Difference Between Measurements at PNC-6 visit") +
  xlab("Average Measurement (g/dl)") + 
  ggtitle('Agreement between PNC-6 Sphb and Hgb')+
  theme_bw() +
  facet_grid(vars(SITE), scales = "free") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  theme(legend.position = "right") + 
    color_scale +
  guides(color = guide_legend(title = NULL))


ggsave('../plots/BAplot_avg.pnc6.jpeg', plot = last_plot(), height = 8, width = 7)
```



```{r eval=FALSE, message=FALSE, include=FALSE}
# INTRACLASS CORRELATION - VISIT 10
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_10, M08_CBC_HB_LBORRES_10) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  icc_results_site <- data.frame(SITE = site, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  icc_results <- rbind(icc_results, icc_results_site)
}
```

```{r eval=FALSE, message=FALSE, include=FALSE}
icc_table <- kable(icc_results, format = "markdown", col.names = c("SITE", "ICC", "Lower", "Upper"), align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

# Add light blue background color to the header row
icc_table <- icc_table %>%
  row_spec(0, background = "lightblue")

icc_table
```

