---
title: "<span style='font-size: 18px'> <span style='text-align: center'> PRISMA Sphb and CBC Hb Intraclass correlation analysis (Issued: `r Sys.Date()`)"
author: 'Author: Fouzia Farooq'
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
---

&nbsp;
&nbsp;
&nbsp;
&nbsp;

\newpage

<br>
**Intraclass correlation:**
<ul>
<li>Reliability index for interrater reliability analysis. It reflects both degree of correlation and agreement between measurements.<li>
<li>Appropriate ICC form must be used since each form involves distinct assumptions and will lead to different interpretations.<li>
<li>These are the assumptions used for form here:<li>
<li>**Model:** Two-way (Mixed-Effects Model) - used when the selected raters (instruments) are the only raters of interest. Results only represent the reliability of the specific instruments involved in the experiment and can't be generalized. 
<li>**Type:** Agreement (agreement: if different instruments assign the same score to the same subject; consistency: instruments' socres to the same group of subjects are correlated in an additive manner.)
<li>**Definition:** Single unit (single rater vs. 'means of k raters').  Single rater type is selected because reliablity experiment involves 2 raters whose average is not as an assessment basis. 

Reliability is defined as the extent to which measurements can be replicated.
In other words, it reflects not only degree of correlation but also agreement between measurements.
Mathematically, reliability represents a ratio of true variance over true variance plus error variance

paper from Masimo: https://www.tandfonline.com/doi/full/10.1080/11101849.2022.2153976


```{css, echo=FALSE}
.table caption {
  color: black;
  font-weight: bold;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(lubridate)
#library(emo)
# library(naniar)
library(dplyr)
library(knitr)
library(kableExtra)
library(irr)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
sphb_df <- read.csv('../data_out/Mat_sphb_20231027.csv')
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# INTRACLASS CORRELATION - ENROLLMENT

icc_df <- sphb_df %>% select(SITE, M06_SPHB_LBORRES_1, M08_CBC_HB_LBORRES_1) 
icc_df %>% group_by(SITE) %>% summarize(N = sum(!is.na(M06_SPHB_LBORRES_1) & !is.na(M08_CBC_HB_LBORRES_1)))

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  
  # Compute the ICC
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  
  # Compute the count of non-missing observations for this site
  icc_n <- site_data %>% summarize(N = sum(!is.na(M06_SPHB_LBORRES_1) & !is.na(M08_CBC_HB_LBORRES_1)))
  
  # Create a data frame with ICC and N
  icc_results_site <- data.frame(SITE = site, N = icc_n$N, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  
    # Combine the results
  icc_results <- rbind(icc_results, icc_results_site)
}

icc_results <- icc_results %>% mutate('95%CI' = paste0("(", format(round(Lower,3),nsmall=2, digits=3), ", ", format(round(Upper,3),nsmall=2, digits=3), ")"))
icc_results <- icc_results %>% rename(Site = SITE) %>% select(-Upper, -Lower)
icc_results$ICC <- format(round(icc_results$ICC, 3), nsmall=2, digits=3)
```


#### Table 1. Intraclass correlation between SpHb and CBC Hb measurements at Enrollment  
```{r echo=FALSE, warning=FALSE}
icc_results  %>% 
   # `rownames<-` (c( 
   #  "Kenya",
   #  "Pakistan",
   #  "Zambia")) %>%
    
     mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;")
  
  # pack_rows("Sphb", 1, 3, label_row_css = "color: steelblue;")
```
<br>
<br>


```{r message=FALSE, warning=FALSE, include=FALSE}
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_2, M08_CBC_HB_LBORRES_2) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  
  # Compute the ICC
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  
  # Compute the count of non-missing observations for this site
  icc_n <- site_data %>% summarize(N = sum(!is.na(M06_SPHB_LBORRES_2) & !is.na(M08_CBC_HB_LBORRES_2)))
  
  # Create a data frame with ICC and N
  icc_results_site <- data.frame(SITE = site, N = icc_n$N, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  
    # Combine the results
  icc_results <- rbind(icc_results, icc_results_site)
}

icc_results <- icc_results %>% mutate('95%CI' = paste0("(", format(round(Lower,3),nsmall=2, digits=3), ", ", format(round(Upper,3),nsmall=2, digits=3), ")"))
icc_results <- icc_results %>% rename(Site = SITE) %>% select(-Upper, -Lower)
icc_results$ICC <- format(round(icc_results$ICC, 3), nsmall=2, digits=3)
```

#### Table 2. Intraclass correlation between SpHb and CBC Hb measurements at ANC-20  
```{r echo=FALSE, warning=FALSE}
icc_results  %>% 
   # `rownames<-` (c( 
   #  "Kenya",
   #  "Pakistan",
   #  "Zambia")) %>%
    
     mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;")
  
  # pack_rows("Sphb", 1, 3, label_row_css = "color: steelblue;")
```
<br>
<br>

```{r message=FALSE, warning=FALSE, include=FALSE}
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_3, M08_CBC_HB_LBORRES_3) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  
  # Compute the ICC
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  
  # Compute the count of non-missing observations for this site
  icc_n <- site_data %>% summarize(N = sum(!is.na(M06_SPHB_LBORRES_3) & !is.na(M08_CBC_HB_LBORRES_3)))
  
  # Create a data frame with ICC and N
  icc_results_site <- data.frame(SITE = site, N = icc_n$N, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  
    # Combine the results
  icc_results <- rbind(icc_results, icc_results_site)
}

icc_results <- icc_results %>% mutate('95%CI' = paste0("(", format(round(Lower,3),nsmall=2, digits=3), ", ", format(round(Upper,3),nsmall=2, digits=3), ")"))
icc_results <- icc_results %>% rename(Site = SITE) %>% select(-Upper, -Lower)
icc_results$ICC <- format(round(icc_results$ICC, 3), nsmall=2, digits=3)
```

#### Table 3. Intraclass correlation between SpHb and CBC Hb measurements at ANC-28  
```{r echo=FALSE, warning=FALSE}
icc_results  %>% 
   # `rownames<-` (c( 
   #  "Kenya",
   #  "Pakistan",
   #  "Zambia")) %>%
    
     mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;")
  
  # pack_rows("Sphb", 1, 3, label_row_css = "color: steelblue;")
```

\newpage

```{r message=FALSE, warning=FALSE, include=FALSE}
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_4, M08_CBC_HB_LBORRES_4)

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  
  # Compute the ICC
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  
  # Compute the count of non-missing observations for this site
  icc_n <- site_data %>% summarize(N = sum(!is.na(M06_SPHB_LBORRES_4) & !is.na(M08_CBC_HB_LBORRES_4)))
  
  # Create a data frame with ICC and N
  icc_results_site <- data.frame(SITE = site, N = icc_n$N, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  
    # Combine the results
  icc_results <- rbind(icc_results, icc_results_site)
}

icc_results <- icc_results %>% mutate('95%CI' = paste0("(", format(round(Lower,3),nsmall=2, digits=3), ", ", format(round(Upper,3),nsmall=2, digits=3), ")"))
icc_results <- icc_results %>% rename(Site = SITE) %>% select(-Upper, -Lower)
icc_results$ICC <- format(round(icc_results$ICC, 3), nsmall=2, digits=3)
```

<br>
<br>

#### Table 4. Intraclass correlation between SpHb and CBC Hb measurements at ANC-32, Pakistan site only  
```{r echo=FALSE, warning=FALSE}
icc_results  %>% 
   # `rownames<-` (c( 
   #  "Kenya",
   #  "Pakistan",
   #  "Zambia")) %>%
    
     mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;")
  
  # pack_rows("Sphb", 1, 3, label_row_css = "color: steelblue;")
```
<br>
<br>

```{r message=FALSE, warning=FALSE, include=FALSE}
icc_df <- sphb_df %>% select( SITE, M06_SPHB_LBORRES_5, M08_CBC_HB_LBORRES_5) 

unique_sites <- unique(icc_df$SITE)
icc_results <- data.frame()

# Loop through each SITE and compute ICC
for (site in unique_sites) {
  site_data <- icc_df %>% filter(SITE == site) %>% select(-SITE)
  
  # Compute the ICC
  icc_value <- icc(site_data, model = "twoway", type = "agreement", unit = "single", conf.level = 0.95)
  
  # Compute the count of non-missing observations for this site
  icc_n <- site_data %>% summarize(N = sum(!is.na(M06_SPHB_LBORRES_5) & !is.na(M08_CBC_HB_LBORRES_5)))
  
  # Create a data frame with ICC and N
  icc_results_site <- data.frame(SITE = site, N = icc_n$N, ICC = icc_value$value, Lower = icc_value$lbound, Upper = icc_value$ubound)
  
    # Combine the results
  icc_results <- rbind(icc_results, icc_results_site)
}

icc_results <- icc_results %>% mutate('95%CI' = paste0("(", format(round(Lower,3),nsmall=2, digits=3), ", ", format(round(Upper,3),nsmall=2, digits=3), ")"))
icc_results <- icc_results %>% rename(Site = SITE) %>% select(-Upper, -Lower)
icc_results$ICC <- format(round(icc_results$ICC, 3), nsmall=2, digits=3)
```

#### Table 5. Intraclass correlation between SpHb and CBC Hb measurements at ANC-36  
```{r echo=FALSE, warning=FALSE}
icc_results  %>% 
   # `rownames<-` (c( 
   #  "Kenya",
   #  "Pakistan",
   #  "Zambia")) %>%
    
     mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;")
  
  # pack_rows("Sphb", 1, 3, label_row_css = "color: steelblue;")
```
